---
title: "AllPWcor"
author: "Rebecca Young"
date: "June 8, 2016"
output: html_document
---

compute all pairwise correlaton
```{r}
PWstageCor<-function(x,y) {
  x<-t(x)
  y<-t(y)
  z<-cor(x,y,use="pairwise.complete.obs", method="spearman")
  return(z)
  }
```

impliment for all comparisons
```{r}
Dan_Gal.cor<-PWstageCor(Dan.shared.OGG.exp, Gal.shared.OGG.exp)
Dan_Mus.cor<-PWstageCor(Dan.shared.OGG.exp, Mus.shared.OGG.exp)
Dan_X.laev.cor<-PWstageCor(Dan.shared.OGG.exp, Xlaev.shared.OGG.exp)
Dan_X.trop.cor<-PWstageCor(Dan.shared.OGG.exp, Xtrop.shared.OGG.exp)

Gal_Mus.cor<-PWstageCor(Gal.shared.OGG.exp, Mus.shared.OGG.exp)
Gal_X.laev.cor<-PWstageCor(Gal.shared.OGG.exp, Xlaev.shared.OGG.exp)
Gal_X.trop.cor<-PWstageCor(Gal.shared.OGG.exp, Xtrop.shared.OGG.exp)

X.laev_Mus.cor<-PWstageCor(Xlaev.shared.OGG.exp,Mus.shared.OGG.exp)
X.trop_Mus.cor<-PWstageCor(Xtrop.shared.OGG.exp,Mus.shared.OGG.exp)

X.laev_trop.cor<-PWstageCor(Xlaev.shared.OGG.exp,Xtrop.shared.OGG.exp)

```

ANOVA comparing PW species correlation strength at different time steps
====================================================================
function to turn the PW matrix of sp-sp correlation into a linear vector
join these into a df 
```{r}
#June 9, 2016 n's: Dan: n=6; Gal: n=5; Mus: n=4; X.laev: n=4; X.trop: n=4 

TimeStep15_PWcorMatix<-function(x,s1n,s2n ) { #here x is the correlation matrix. y defines the steps SPECIES SPECIFIC
  early<-x[c(1:s1n),c(1:s2n)]
  middle<-x[c((s1n+1): (15-s1n)) , c((s2n+1):(15-s2n))]
  late<-x[c((16-s1n): 15) , c((16-s2n):15)]
  
  early[lower.tri(early,diag = TRUE)]<-NA
  middle[lower.tri(middle,diag = TRUE)]<-NA
  late[lower.tri(late,diag = TRUE)]<-NA

  cor<-as.vector(early)
  cor<-na.omit(cor)
  cor<-data.matrix(cor)  
  time<-rep(c('early'), c(length(cor)))
  early<-data.frame(time, cor)
  
  cor<-as.vector(middle)
  cor<-na.omit(cor)
  cor<-data.matrix(cor)
  time<-rep(c('middle'), c(length(cor)))
  middle<-data.frame(time, cor)
  
  cor<-as.vector(late)
  cor<-na.omit(cor)
  cor<-data.matrix(cor)
  time<-rep(c('late'), c(length(cor)))
  late<-data.frame(time, cor)
  
  timesteps<-rbind(early,middle,late)
  return(timesteps)
  }
  
TimeStep19_PWcorMatix<-function(x,s1n,s2n ) { #here x is the correlation matrix. y defines the steps SPECIES SPECIFIC
  early<-x[c(1:s1n),c(1:s2n)]
  middle<-x[c((s1n+1): (15-s1n)) , c((s2n+1):(19-s2n))]
  late<-x[c((16-s1n): 15) , c((20-s2n):19)]
  
  early[lower.tri(early,diag = TRUE)]<-NA
  middle[lower.tri(middle,diag = TRUE)]<-NA
  late[lower.tri(late,diag = TRUE)]<-NA

  cor<-as.vector(early)
  cor<-na.omit(cor)
  cor<-data.matrix(cor)  
  time<-rep(c('early'), c(length(cor)))
  early<-data.frame(time, cor)
  
  cor<-as.vector(middle)
  cor<-na.omit(cor)
  cor<-data.matrix(cor)
  time<-rep(c('middle'), c(length(cor)))
  middle<-data.frame(time, cor)
  
  cor<-as.vector(late)
  cor<-na.omit(cor)
  cor<-data.matrix(cor)
  time<-rep(c('late'), c(length(cor)))
  late<-data.frame(time, cor)
  
  timesteps<-rbind(early,middle,late)
  return(timesteps)
  }
```

generate aov datasets
```{r}

#June 9, 2016 n's: Dan: n=6; Gal: n=5; Mus: n=4; X.laev: n=4; X.trop: n=4 
Dan_Gal.TimeCor<-TimeStep15_PWcorMatix(Dan_Gal.cor,6,5)
Dan_Mus.TimeCor<-TimeStep19_PWcorMatix(Dan_Mus.cor,6,4)
Dan_Xlaev.TimeCor<-TimeStep15_PWcorMatix(Dan_X.laev.cor,6,4)
Dan_Xtrop.TimeCor<-TimeStep15_PWcorMatix(Dan_X.trop.cor,6,4)

Gal_Mus.TimeCor<-TimeStep19_PWcorMatix(Gal_Mus.cor,5,4)
Gal_Xlaev.TimeCor<-TimeStep15_PWcorMatix(Gal_X.laev.cor,5,4)
Gal_Xtrop.TimeCor<-TimeStep15_PWcorMatix(Gal_X.trop.cor,5,4)

Xlaev_Mus.TimeCor<-TimeStep19_PWcorMatix(X.laev_Mus.cor,4,4)
Xtrop_Mus.TimeCor<-TimeStep19_PWcorMatix(X.trop_Mus.cor,4,4)

Xlaev_Xtrop.TimeCor<-TimeStep15_PWcorMatix(X.laev_trop.cor,4,4)

All.TimeCor_Xtrop<-rbind(Dan_Gal.TimeCor, Dan_Mus.TimeCor,Dan_Xlaev.TimeCor, Dan_Xtrop.TimeCor,Gal_Mus.TimeCor,Gal_Xlaev.TimeCor,Gal_Xtrop.TimeCor,Xlaev_Mus.TimeCor,Xtrop_Mus.TimeCor, Xlaev_Xtrop.TimeCor)

All.TimeCor<-rbind(Dan_Gal.TimeCor, Dan_Mus.TimeCor,Dan_Xlaev.TimeCor, Gal_Mus.TimeCor,Gal_Xlaev.TimeCor,Xlaev_Mus.TimeCor)

library("plyr")
Dan_Gal.TimeCor_means<-ddply(Dan_Gal.TimeCor,~time,summarise,cor=mean(cor))
Dan_Mus.TimeCor_means<-ddply(Dan_Mus.TimeCor,~time,summarise,cor=mean(cor))
Dan_Xlaev.TimeCor_means<-ddply(Dan_Xlaev.TimeCor,~time,summarise,cor=mean(cor))
Dan_Xtrop.TimeCor_means<-ddply(Dan_Xtrop.TimeCor,~time,summarise,cor=mean(cor))

Gal_Mus.TimeCor_means<-ddply(Gal_Mus.TimeCor,~time,summarise,cor=mean(cor))
Gal_Xlaev.TimeCor_means<-ddply(Gal_Xlaev.TimeCor,~time,summarise,cor=mean(cor))
Gal_Xtrop.TimeCor_means<-ddply(Gal_Xtrop.TimeCor,~time,summarise,cor=mean(cor))

Xlaev_Mus.TimeCor_means<-ddply(Xlaev_Mus.TimeCor,~time,summarise,cor=mean(cor))
Xtrop_Mus.TimeCor_means<-ddply(Xtrop_Mus.TimeCor,~time,summarise,cor=mean(cor))

Xlaev_Xtrop.TimeCor_means<-ddply(Xlaev_Xtrop.TimeCor,~time,summarise,cor=mean(cor))

All.TimeCor_means<-rbind(Dan_Gal.TimeCor_means, Dan_Mus.TimeCor_means,Dan_Xlaev.TimeCor_means, Dan_Xtrop.TimeCor_means,Gal_Mus.TimeCor_means,Gal_Xlaev.TimeCor_means,Gal_Xtrop.TimeCor_means,Xlaev_Mus.TimeCor_means,Xtrop_Mus.TimeCor_means, Xlaev_Xtrop.TimeCor_means)

```

run anova for each species pair; TukeyHSD for significance

```{r}
Dan_Gal.TimeCor_AOV<-aov(cor~time, data=Dan_Gal.TimeCor)
Dan_Mus.TimeCor_AOV<-aov(cor~time, data=Dan_Mus.TimeCor)
Dan_Xlaev.TimeCor_AOV<-aov(cor~time, data=Dan_Xlaev.TimeCor)
Dan_Xtrop.TimeCor_AOV<-aov(cor~time, data=Dan_Xtrop.TimeCor)

Gal_Mus.TimeCor_AOV<-aov(cor~time, data=Gal_Mus.TimeCor)
Gal_Xlaev.TimeCor_AOV<-aov(cor~time, data=Gal_Xlaev.TimeCor)
Gal_Xtrop.TimeCor_AOV<-aov(cor~time, data=Gal_Xtrop.TimeCor)

Xlaev_Mus.TimeCor_AOV<-aov(cor~time, data=Xlaev_Mus.TimeCor)
Xtrop_Mus.TimeCor_AOV<-aov(cor~time, data=Xtrop_Mus.TimeCor)

Xlaev_Xtrop.TimeCor_AOV<-aov(cor~time, data=Xlaev_Xtrop.TimeCor)

All.TimeCor_AOV<-aov(cor~time, data=All.TimeCor)
summary(All.TimeCor_AOV)
TukeyHSD(All.TimeCor_AOV)

All.TimeCor_means_AOV<-aov(cor~time, data=All.TimeCor_means)
summary(All.TimeCor_means_AOV)
TukeyHSD(All.TimeCor_means_AOV)
```

Re-create Irie & Kuritani figure 
```{r}
cor<-c((Dan_Gal.cor[12,15]), (Dan_Mus.cor[12,19]), (Dan_X.laev.cor[12,15]), (Gal_Mus.cor[15,19]), (Gal_X.laev.cor[15,15]),  (X.laev_Mus.cor[15,19]))
time<-rep(c('latest'), c(length(cor)))
 
latest<-data.frame(time,cor)

cor<-c((Dan_Gal.cor[8,8]), (Dan_Mus.cor[8,7]), (Dan_Mus.cor[8,7]), (Dan_X.laev.cor[8,10]), (Gal_Mus.cor[8,7]), (Gal_X.laev.cor[8,10]),  (X.laev_Mus.cor[10,7]))
time<-rep(c('pharyngula'), c(length(cor)))
 
pharyngula<-data.frame(time,cor)
 
cor<-c((Dan_Gal.cor[2,1]), (Dan_Mus.cor[2,4]), (Dan_X.laev.cor[2,3]),  (Gal_Mus.cor[1,4]), (Gal_X.laev.cor[1,3]),  (X.laev_Mus.cor[3,4]))
time<-rep(c('blastula_shield'), c(length(cor)))
 
blastula_shield<-data.frame(time,cor)
 
cor<-c((Dan_Mus.cor[1,2]), (Dan_X.laev.cor[1,1]), (X.laev_Mus.cor[1,2]))
time<-rep(c('cleavage'), c(length(cor)))
 
cleavage<-data.frame(time,cor)

IK_timesteps<-rbind(latest, pharyngula, blastula_shield, cleavage)
IK_timesteps_AOV<-aov(cor~time, data=IK_timesteps)
summary(IK_timesteps_AOV)
TukeyHSD(IK_timesteps_AOV)
```

Re-create Irie & Kuritani figure (with X. trop)
```{r}
cor<-c((Dan_Gal.cor[12,15]), (Dan_Mus.cor[12,15]), (Dan_X.laev.cor[12,15]), (Dan_X.trop.cor[12,15]), (Gal_Mus.cor[15,19]), (Gal_X.laev.cor[15,15]), (Gal_X.trop.cor[15,15]), (X.laev_Mus.cor[15,19]), (X.laev_trop.cor[15,15]), (X.trop_Mus.cor[15,19]))
time<-rep(c('latest'), c(length(cor)))
 
latest<-data.frame(time,cor)

cor<-c((Dan_Gal.cor[8,8]), (Dan_Mus.cor[8,7]),  (Dan_X.laev.cor[8,10]), (Dan_X.trop.cor[8,10]), (Gal_Mus.cor[8,7]), (Gal_X.laev.cor[8,10]), (Gal_X.trop.cor[8,10]), (X.laev_Mus.cor[10,7]), (X.laev_trop.cor[10,10]), (X.trop_Mus.cor[10,7]))
time<-rep(c('pharyngula'), c(length(cor)))
 
pharyngula<-data.frame(time,cor)
 
cor<-c((Dan_Gal.cor[2,1]), (Dan_Mus.cor[2,4]),  (Dan_X.laev.cor[2,3]), (Dan_X.trop.cor[2,3]), (Gal_Mus.cor[1,4]), (Gal_X.laev.cor[1,3]), (Gal_X.trop.cor[1,3]), (X.laev_Mus.cor[3,4]), (X.laev_trop.cor[3,3]), (X.trop_Mus.cor[3,4]))
time<-rep(c('blastula_shield'), c(length(cor)))
 
blastula_shield<-data.frame(time,cor)
 
cor<-c((Dan_Mus.cor[1,2]), (Dan_X.laev.cor[1,1]), (Dan_X.trop.cor[1,1]), (X.laev_Mus.cor[1,2]), (X.laev_trop.cor[1,1]), (X.trop_Mus.cor[1,2]))
time<-rep(c('cleavage'), c(length(cor)))
 
cleavage<-data.frame(time,cor)

IK_timesteps_Xtrop<-rbind(latest, pharyngula, blastula_shield, cleavage)
test<-IK_timesteps_Xtrop
test$time<-factor(test$time, levels=c("cleavage", "blastula_shield", "pharyngula", "latest"))

IK_timesteps_Xtrop_AOV<-aov(cor~time, data=IK_timesteps)
summary(IK_timesteps_Xtrop_AOV)
TukeyHSD(IK_timesteps_Xtrop_AOV)
```
Plots
```{r}
scale_fill_manual(values=c('#addd8e','#31a354','#006837'))

library("ggplot2")
pdf("Allsp_SpearmanCorXTime")
ggplot(All.TimeCor, aes(x = time, y = cor, fill=time)) + 
geom_boxplot() + scale_fill_manual(values=c('#f7fcb9','#41ab5d','#005a32'))+ geom_jitter()+
theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank()) 
dev.off()

##need to reverse the order!

pdf("IK_replication")
ggplot(IK_timesteps, aes(x = time, y = cor, fill=time)) + 
geom_boxplot() + geom_jitter()+ scale_fill_manual(values=c('#f7fcb9','#addd8e','#41ab5d','#005a32'))+ 
  theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank()) 
dev.off()

```
