---
title: "HourglassPhyloComparison"
author: "Becca"
date: "March 9, 2017"
output: html_document
---
## R Markdown

Analyses associated with assessing the relationship between phylgenetic distance and embryonic distance. 
```{r}
library("reshape2")
library("ggplot2")
#phylo_distance=distance
#row.names(phylo_distance)<-row.names(AllClustCor4)
#rm(distance)
#SPpair=data.frame(row.names(AllClustCor4))
#colnames(SPpair)<-"SPpair"
phylo_distance<-cbind.data.frame(row.names(phylo_distance), phylo_distance)


AllClustCor4_phydist<-cbind.data.frame(SPpair,AllClustCor4)
AllClustCor4_phydist<-melt(AllClustCor4_phydist, id="SPpair")
x<-cbind.data.frame(rep(phylo_distance$SPpair, 4), rep(phylo_distance$distance,4))
colnames(x)<-c("SPpair", "distance")
AllClustCor4_phydist<-merge(AllClustCor4_phydist, x, by="SPpair")
  
AllClustCor5_phydist<-cbind.data.frame(SPpair,AllClustCor5)
AllClustCor5_phydist<-melt(AllClustCor5_phydist, id="SPpair")
x<-cbind.data.frame(rep(phylo_distance$SPpair, 5), rep(phylo_distance$distance,5))
colnames(x)<-c("SPpair", "distance")
AllClustCor5_phydist<-merge(AllClustCor5_phydist, x, by="SPpair")
```


```{r, echo=FALSE}

ggplot(AllClustCor4_phydist, aes(x=distance, y=value,  group=variable, colour=variable))+
  geom_point(aes(size=0.75), shape=1)+
  geom_smooth(method=lm, se=FALSE)+
  scale_colour_hue(l=50)+
    ylab("rank correlation")+
    xlab("phylogenetic distance")+
    theme_bw() + 
    theme(axis.title.x=element_blank(),
        axis.text.x=element_text(size=10,face="plain", 
                                 color="black"),
        axis.text.y=element_text(size=14,
                                 face="plain"),
        axis.title.y=element_text(size=18,
                                  face="bold"),
        panel.grid.major=element_blank(),
        panel.grid.minor = element_blank(),
        panel.border=element_rect(fill=NA, 
                                  size=0.5,
                                  color ="black"))


pdf("PhyloHour_allSP.pdf", useDingbats = FALSE)
ggplot(AllClustCor5_phydist, aes(x=distance, y=value,  group=variable, colour=variable))+
  geom_point(aes(size=0.75), shape=1)+
  geom_smooth(method=lm, se=FALSE)+
  scale_colour_hue(l=50)+
    ylab("rank correlation")+
    xlab("phylogenetic distance")+
    theme_bw() + 
    theme(axis.title.x=element_blank(),
        axis.text.x=element_text(size=10,face="plain", 
                                 color="black"),
        axis.text.y=element_text(size=14,
                                 face="plain"),
        axis.title.y=element_text(size=18,
                                  face="bold"),
        panel.grid.major=element_blank(),
        panel.grid.minor = element_blank(),
        panel.border=element_rect(fill=NA, 
                                  size=0.5,
                                  color ="black"))
dev.off()
    
```

same as above, but remove Xlaev and Xtrop

```{r, remove the Xenopus}
library("dplyr")
  x<- AllClustCor4_phydist %>% 
  dplyr::filter(SPpair != "XlaevXtrop")
  
    y<- AllClustCor5_phydist %>% 
  dplyr::filter(SPpair != "XlaevXtrop")
    
pdf("PhyloHour_NOlaevtrop.pdf", useDingbats = FALSE)
ggplot(x, aes(x=distance, y=value,  group=variable, colour=variable))+
  geom_point(aes(size=0.75), shape=1)+
  geom_smooth(method=lm, se=FALSE)+
  scale_colour_hue(l=50)+
    ylab("rank correlation")+
    xlab("phylogenetic distance")+
    theme_bw() + 
    theme(axis.title.x=element_blank(),
        axis.text.x=element_text(size=10,face="plain", 
                                 color="black"),
        axis.text.y=element_text(size=14,
                                 face="plain"),
        axis.title.y=element_text(size=18,
                                  face="bold"),
        panel.grid.major=element_blank(),
        panel.grid.minor = element_blank(),
        panel.border=element_rect(fill=NA, 
                                  size=0.5,
                                  color ="black"))  
  
  
ggplot(y, aes(x=distance, y=value,  group=variable, colour=variable))+
  geom_point(aes(size=0.75), shape=1)+
  geom_smooth(method=lm, se=FALSE)+
  scale_colour_hue(l=50)+
    ylab("rank correlation")+
    xlab("phylogenetic distance")+
    theme_bw() + 
    theme(axis.title.x=element_blank(),
        axis.text.x=element_text(size=10,face="plain", 
                                 color="black"),
        axis.text.y=element_text(size=14,
                                 face="plain"),
        axis.title.y=element_text(size=18,
                                  face="bold"),
        panel.grid.major=element_blank(),
        panel.grid.minor = element_blank(),
        panel.border=element_rect(fill=NA, 
                                  size=0.5,
                                  color ="black"))
dev.off()
  

```
same as above but remove "XlaevXtrop" and "MusGal"
```{r, remove Xenopus and MusGal comparisons}
library("dplyr")
  x<- AllClustCor4_phydist %>% 
  dplyr::filter(SPpair != "XlaevXtrop") %>%
  dplyr::filter(SPpair != "MusGal")

  y<- AllClustCor5_phydist %>% 
  dplyr::filter(SPpair != "XlaevXtrop") %>%
  dplyr::filter(SPpair != "MusGal")
 
  pdf("PhyloHour_NOlaevtropMusGal.pdf", useDingbats = FALSE) 
  ggplot(x, aes(x=distance, y=value,  group=variable, colour=variable))+
  geom_point(aes(size=0.75), shape=1)+
  geom_smooth(method=lm, se=FALSE)+
  scale_colour_hue(l=50)+
    ylab("rank correlation")+
    xlab("phylogenetic distance")+
    theme_bw() + 
    theme(axis.title.x=element_blank(),
        axis.text.x=element_text(size=10,face="plain", 
                                 color="black"),
        axis.text.y=element_text(size=14,
                                 face="plain"),
        axis.title.y=element_text(size=18,
                                  face="bold"),
        panel.grid.major=element_blank(),
        panel.grid.minor = element_blank(),
        panel.border=element_rect(fill=NA, 
                                  size=0.5,
                                  color ="black"))
  
  ggplot(y, aes(x=distance, y=value,  group=variable, colour=variable))+
  geom_point(aes(size=0.75), shape=1)+
  geom_smooth(method=lm, se=FALSE)+
  scale_colour_hue(l=50)+
    ylab("rank correlation")+
    xlab("phylogenetic distance")+
    theme_bw() + 
    theme(axis.title.x=element_blank(),
        axis.text.x=element_text(size=10,face="plain", 
                                 color="black"),
        axis.text.y=element_text(size=14,
                                 face="plain"),
        axis.title.y=element_text(size=18,
                                  face="bold"),
        panel.grid.major=element_blank(),
        panel.grid.minor = element_blank(),
        panel.border=element_rect(fill=NA, 
                                  size=0.5,
                                  color ="black"))
  dev.off()
```
phylo distance to the random data. make a scatter plot of data by cluster for each cluster. compare random (line with CI) to real (line with CI) do this for the three plots without XlaevXtrop, w/o XlaveXtrop and MusGal
```{r, include random data}
library("ggplot2")
library("reshape2")
x=K5SPvar_summary
y=AllClustCor5_phydist
z=phylo_distance

Phylo_scatter_RankCor_RandxRealclust<-function(x,y,z){ 
  x<-melt(x,id="SPpair")
  x<-merge(x,z, by="SPpair")
  df_x<-cbind.data.frame(x, 
                         data.frame(rep("random", 
                                        length(x$SPpair))))
  names(df_x) <- c("SPpair",
                   "cluster", 
                   "correlation", 
                   "distance", 
                   "type")

  df_y<-cbind.data.frame(y, 
                         data.frame(rep("real", 
                                        length(y$SPpair))))
  names(df_y) <- c("SPpair",
                   "cluster", 
                   "correlation", 
                   "distance", 
                   "type")
  df<-rbind.data.frame(df_x,df_y)
  clusters<-unique(df$cluster)
  
  for (i in seq_along(clusters)){
  plot=ggplot(subset(df, df$cluster==clusters[i]), 
         aes(x=distance, 
             y=correlation, 
             group=type,
             color=type))+
    geom_point(shape = 1, lwd=5, stroke=1.5)+
    geom_smooth(method=lm,
              alpha=0.25,
               aes(color = type, 
                  group = type, 
                    fill= type)) +
    ylab("rank correlation")+  
    theme_bw() + 
    theme(axis.title.x=element_blank(),
        axis.text.x=element_text(size=18,face="plain", 
                                 color="black"),
        axis.text.y=element_text(size=14,
                                 face="plain"),
        axis.title.y=element_text(size=18,
                                  face="bold"),
        panel.grid.major=element_blank(),
        panel.grid.minor = element_blank(),
        panel.border=element_rect(fill=NA, 
                                  size=0.5,
                                  color ="black"))+
    ggtitle(paste(clusters[i], 
                    sep=''))
  print(plot)}
  }

pdf("Phylo-Cor_scatterBYcluster_ALL.pdf", useDingbats = FALSE)
Phylo_scatter_RankCor_RandxRealclust(K5SPvar_summary,
                                     AllClustCor5_phydist,
                                     phylo_distance)
dev.off()
 
pdf("Phylo-Cor_scatterBYcluster_NOlaevtrop.pdf", useDingbats = FALSE)
Phylo_scatter_RankCor_RandxRealclust(K5SPvar_summary %>% 
                                       dplyr::filter(SPpair != "XlaevXtrop"),
                                     AllClustCor5_phydist %>% 
                                       dplyr::filter(SPpair != "XlaevXtrop"),
                                     phylo_distance)
dev.off()

pdf("Phylo-Cor_scatterBYcluster_NOlaevtropMusGal.pdf", useDingbats = FALSE)
Phylo_scatter_RankCor_RandxRealclust(K5SPvar_summary %>% 
                                       dplyr::filter(SPpair != "XlaevXtrop") %>% 
                                       dplyr::filter(SPpair != "MusGal"),
                                     AllClustCor5_phydist %>% 
                                       dplyr::filter(SPpair != "XlaevXtrop") %>% 
                                       dplyr::filter(SPpair != "MusGal"),
                                     phylo_distance)
dev.off()  

```