---
title: "KstageVarianceCompare"
author: "Becca"
date: "Tuesday, December 06, 2016"
output: html_document
---

Function using plyr, takes OGG expression data, stage clustering, and k (number of clusters), calculates OGG variance for each OGG in each of k clusters (stagesClustVarWI). Second function (stagesClustVarAS) take mean of each OGG for each of k clusters in each species, then a variance of those means across species.  


```{r}
library("plyr")
#caluclates the within species variane of each OGG for k clusters
stageClustVarWI<-function(a, a1, b, b1, c, c1, 
                        d, d1, e, e1, k, spA, 
                        spB, spC, spD, spE){
CV<-function(x) {(var(x)/mean(x))*100}
a1<-a1[,c(1,2,k+1)]
colnames(a1)=c("species", "timepoint", "k")
a=cbind.data.frame(a, timepoint=row.names(a))
ak=merge(a1, a, by='timepoint', all=FALSE)
ak=ak[,-c(1:2)]
ak1= ddply(ak,  "k", 
           function(x) {
             y=subset(x, select=-k)
             apply(y,2,CV)})
ak1<-cbind.data.frame(ak1, "species"=rep(spA, k))
ak1=ak1[,c(ncol(ak1),1:ncol(ak1)-1)]

b1<-b1[,c(1,2,k+1)]
colnames(b1)=c("species", "timepoint", "k")
b=cbind.data.frame(b, timepoint=row.names(b))
bk=merge(b1, b,by='timepoint', all=FALSE)
bk=bk[,-c(1:2)]
bk1= ddply(bk,  "k", 
           function(x) {
             y=subset(x, select=-k)
             apply(y,2,CV)})
bk1<-cbind.data.frame(bk1, "species"=rep(spB, k))
bk1=bk1[,c(ncol(bk1),1:ncol(bk1)-1)]

c1<-c1[,c(1,2,k+1)]
colnames(c1)=c("species", "timepoint", "k")
c=cbind.data.frame(c, timepoint=row.names(c))
ck=merge(c1, c,by='timepoint', all=FALSE)
ck=ck[,-c(1:2)]
ck1= ddply(ck,  "k", 
           function(x) {
             y=subset(x, select=-k)
             apply(y,2,CV)})
ck1<-cbind.data.frame(ck1, "species"=rep(spC, k))
ck1=ck1[,c(ncol(ck1),1:ncol(ck1)-1)]

d1=d1[,c(1,2,k+1)]
colnames(d1)=c("species", "timepoint", "k")
d=cbind.data.frame(d, timepoint=d1$timepoint)
dk=merge(d1, d,by='timepoint', all=FALSE)
dk=dk[,-c(1:2)]
dk1= ddply(dk,  "k", 
           function(x) {
             y=subset(x, select=-k)
             apply(y,2,CV)})
dk1<-cbind.data.frame(dk1, "species"=rep(spD, k))
dk1=dk1[,c(ncol(dk1),1:ncol(dk1)-1)]

e1=e1[,c(1,2,k+1)]
colnames(e1)=c("species", "timepoint", "k")
e=cbind.data.frame(e, timepoint=e1$timepoint)
ek=merge(e1, e,by='timepoint', all=FALSE)
ek=ek[,-c(1:2)]
ek1= ddply(ek,  "k", 
           function(x) {
             y=subset(x, select=-k)
             apply(y,2,CV)})
ek1<-cbind.data.frame(ek1, "species"=rep(spE, k))
ek1=ek1[,c(ncol(ek1),1:ncol(ek1)-1)]

all=rbind.data.frame(ak1, bk1, ck1, dk1, ek1)
return(all)
}



stageClustVarAS<-function(a, a1, b, b1, c, c1, 
                        d, d1, e, e1, k){
  CV<-function(x) {(var(x)/mean(x))*100}
  a1<-a1[,c(1,2,k+1)]
colnames(a1)=c("species", "timepoint", "k")
a=cbind.data.frame(a, timepoint=row.names(a))
ak=merge(a1, a, by='timepoint', all=FALSE)
ak=ak[,-c(1:2)]
ak1= ddply(ak,  "k", 
           function(x) {
             y=subset(x, select=-k)
             apply(y,2,mean)})

b1<-b1[,c(1,2,k+1)]
colnames(b1)=c("species", "timepoint", "k")
b=cbind.data.frame(b, timepoint=row.names(b))
bk=merge(b1, b,by='timepoint', all=FALSE)
bk=bk[,-c(1:2)]
bk1= ddply(bk,  "k", 
           function(x) {
             y=subset(x, select=-k)
             apply(y,2,mean)})

c1<-c1[,c(1,2,k+1)]
colnames(c1)=c("species", "timepoint", "k")
c=cbind.data.frame(c, timepoint=row.names(c))
ck=merge(c1, c,by='timepoint', all=FALSE)
ck=ck[,-c(1:2)]
ck1= ddply(ck,  "k", 
           function(x) {
             y=subset(x, select=-k)
             apply(y,2,mean)})


d1=d1[,c(1,2,k+1)]
colnames(d1)=c("species", "timepoint", "k")
d=cbind.data.frame(d, timepoint=row.names(d))
dk=merge(d1, d,by='timepoint', all=FALSE)
dk=dk[,-c(1:2)]
dk1= ddply(dk,  "k", 
           function(x) {
             y=subset(x, select=-k)
             apply(y,2,mean)})


e1=e1[,c(1,2,k+1)]
colnames(e1)=c("species", "timepoint", "k")
e=cbind.data.frame(e, timepoint=row.names(e))
ek=merge(e1, e,by='timepoint', all=FALSE)
ek=ek[,-c(1:2)]
ek1= ddply(ek,  "k", 
           function(x) {
             y=subset(x, select=-k)
             apply(y,2,mean)})

all=rbind.data.frame(ak1, bk1, ck1, dk1, ek1)
allvar= ddply(all,  "k", 
           function(x) {
             y=subset(x, select=-k)
             apply(y,2,CV)})
allvar<-cbind.data.frame(allvar, "species"=rep("all", k))
allvar=allvar[,c(ncol(allvar),1:ncol(allvar)-1)]
return(allvar)
}

```

For K's 3 to 6 run stageClustVarWI and stageClustVarAS and rbind them
"...ClusterID" dfs are generated using kmeans_ALLOGGs_stages function in (Kmeans_Stages.Rmd)
OGGs selected using OGGselection_CV_FC.Rmd

All OGGs
```{r}
stageVark3WI<-stageClustVarWI(Mus.shared.OGG.exp, Mus_clusterID, 
                                             Gal.shared.OGG.exp, Gallus_clusterID,
                                             Dan.shared.OGG.exp, Danio_clusterID, 
                                             Xlaev.shared.OGG.exp, Xlaev_clusterID, 
                                             Xtrop.shared.OGG.exp, Xtrop_clusterID, 
                                             3, "Mus", "Gallus", "Danio", "Xlaev", "Xtrop")
stageVark3WI[is.na(stageVark3WI)] <- 0 #if a cluster has only one stage the variance is 0
                               
stageVark3AS<-stageClustVarAS(Mus.shared.OGG.exp, Mus_clusterID, 
                                             Gal.shared.OGG.exp, Gallus_clusterID,
                                             Dan.shared.OGG.exp, Danio_clusterID, 
                                             Xlaev.shared.OGG.exp, Xlaev_clusterID, 
                                             Xtrop.shared.OGG.exp, Xtrop_clusterID,3)

stageVark4AS<-stageClustVarAS(Mus.shared.OGG.exp, Mus_clusterID, 
                                             Gal.shared.OGG.exp, Gallus_clusterID,
                                             Dan.shared.OGG.exp, Danio_clusterID, 
                                             Xlaev.shared.OGG.exp, Xlaev_clusterID, 
                                             Xtrop.shared.OGG.exp, Xtrop_clusterID,4)

stageVark5AS<-stageClustVarAS(Mus.shared.OGG.exp, Mus_clusterID, 
                                             Gal.shared.OGG.exp, Gallus_clusterID,
                                             Dan.shared.OGG.exp, Danio_clusterID, 
                                             Xlaev.shared.OGG.exp, Xlaev_clusterID, 
                                             Xtrop.shared.OGG.exp, Xtrop_clusterID,5)

stageVark6AS<-stageClustVarAS(Mus.shared.OGG.exp, Mus_clusterID, 
                                             Gal.shared.OGG.exp, Gallus_clusterID,
                                             Dan.shared.OGG.exp, Danio_clusterID, 
                                             Xlaev.shared.OGG.exp, Xlaev_clusterID, 
                                             Xtrop.shared.OGG.exp, Xtrop_clusterID,6)

```

For K's 3 to 6 run stageClustVarWI and stageClustVarAS and rbind them
"...ClusterID" dfs are OGGs selected using OGGselection_CV_FC.Rmd

top ten 
```{r}
#Time groupings were generated OGGselection_CV_FC.Rmd
stageVark3WI90<-stageClustVarWI(Mus.shareTime90, Mus_clusterID, 
                                             Gal.shareTime90, Gallus_clusterID,
                                             Dan.shareTime90, Danio_clusterID, 
                                             Xlaev.shareTime90, Xlaev_clusterID, 
                                             Xtrop.shareTime90, Xtrop_clusterID, 
                                             3, "Mus", "Gallus", "Danio", "Xlaev", "Xtrop")
stageVark3WI90[is.na(stageVark3WI90)] <- 0


stageVark3AS90<-stageClustVarAS(Mus.shareTime90, Mus_clusterID, 
                                             Gal.shareTime90, Gallus_clusterID,
                                             Dan.shareTime90, Danio_clusterID, 
                                             Xlaev.shareTime90, Xlaev_clusterID, 
                                             Xtrop.shareTime90, Xtrop_clusterID,3)

stageVark4WI90<-stageClustVarWI(Mus.shareTime90, Mus_clusterID, 
                                             Gal.shareTime90, Gallus_clusterID,
                                             Dan.shareTime90, Danio_clusterID, 
                                             Xlaev.shareTime90, Xlaev_clusterID, 
                                             Xtrop.shareTime90, Xtrop_clusterID, 
                                             4, "Mus", "Gallus", "Danio", "Xlaev", "Xtrop")
stageVark4WI90[is.na(stageVark4WI90)] <- 0

stageVark4AS90<-stageClustVarAS(Mus.shareTime90, Mus_clusterID, 
                                             Gal.shareTime90, Gallus_clusterID,
                                             Dan.shareTime90, Danio_clusterID, 
                                             Xlaev.shareTime90, Xlaev_clusterID, 
                                             Xtrop.shareTime90, Xtrop_clusterID,4)

stageVark5WI90<-stageClustVarWI(Mus.shareTime90, Mus_clusterID, 
                                             Gal.shareTime90, Gallus_clusterID,
                                             Dan.shareTime90, Danio_clusterID, 
                                             Xlaev.shareTime90, Xlaev_clusterID, 
                                             Xtrop.shareTime90, Xtrop_clusterID, 
                                             5, "Mus", "Gallus", "Danio", "Xlaev", "Xtrop")
stageVark5WI90[is.na(stageVark5WI90)] <- 0

stageVark5AS90<-stageClustVarAS(Mus.shareTime90, Mus_clusterID, 
                                             Gal.shareTime90, Gallus_clusterID,
                                             Dan.shareTime90, Danio_clusterID, 
                                             Xlaev.shareTime90, Xlaev_clusterID, 
                                             Xtrop.shareTime90, Xtrop_clusterID,5)


stageVark6AS90<-stageClustVarAS(Mus.shareTime90, Mus_clusterID, 
                                             Gal.shareTime90, Gallus_clusterID,
                                             Dan.shareTime90, Danio_clusterID, 
                                             Xlaev.shareTime90, Xlaev_clusterID, 
                                             Xtrop.shareTime90, Xtrop_clusterID,6)


```
scatter plot
```{r}
library("reshape2")
library("ggplot2")

#x=withinSpecies Variance; y=Across Species Variance, n = cluster number, p= point size
scatterWIonAS<-function(x,y,n, p){
  df1<-melt(x, id=c("species", "k"))
  colnames(df1)<-c("species", "k", "OGG", "withinVar")
  df2<-melt(y, id=c("species", "k"))
  df2<-df2[,-1]
  colnames(df2)<-c("k", "OGG", "acrossVar")
  df<-merge(df1, df2, by=c("OGG", "k"), keep=TRUE)
  plot<-ggplot(data=subset(df, k==n), aes(x=(acrossVar), y=(withinVar), 
                                          group = species, colour = species)) +
    geom_point( size=4, shape=19)+
    theme_bw()+ theme(panel.border = element_blank(), plot.background = element_blank(),
                    panel.grid.major=element_blank(), 
                    panel.grid.minor=element_blank()) + 
    theme(axis.line.x =element_line(color = "black"))+
    theme(axis.line.y =element_line(color = "black"))+
    labs(x="Interspecific Variance", y="Intraspecific Variance")
  return(plot)
  }

scatterWIonAS(stageVark3WI90, stageVark3AS90,1,5)
scatterWIonAS(stageVark3WI90, stageVark3AS90,2,5)
scatterWIonAS(stageVark3WI90, stageVark3AS90,3,5)

scatterWIonAS(stageVark4WI90, stageVark4AS90,1,5)
scatterWIonAS(stageVark4WI90, stageVark4AS90,2,5)
scatterWIonAS(stageVark4WI90, stageVark4AS90,3,5)
scatterWIonAS(stageVark4WI90, stageVark4AS90,4,5)

scatterWIonAS(stageVark5WI90, stageVark5AS90,1,5)
scatterWIonAS(stageVark5WI90, stageVark5AS90,2,5)
scatterWIonAS(stageVark5WI90, stageVark5AS90,3,5)
scatterWIonAS(stageVark5WI90, stageVark5AS90,4,5)
scatterWIonAS(stageVark5WI90, stageVark5AS90,5,5)

```


```{r}
library("reshape2")
library("ggplot2")
boxAS<-function(y){
  df<-melt(y, id=c("species", "k"))
  df<-df[,-1]
  colnames(df)<-c("k", "OGG", "acrossVar")
  df$k<-as.factor(df$k)
  plot<-ggplot(df, aes(x=k, y=(acrossVar)))+
    geom_boxplot()+
    ylab("CV in expression across species")+  
    theme_bw() + 
    theme(axis.title.x=element_blank(),
        axis.text.x=element_text(size=18,face="plain", 
                                 color="black"),
        axis.text.y=element_text(size=14,
                                 face="plain"),
        axis.title.y=element_text(size=18,
                                  face="bold"),
        panel.grid.major=element_blank(),
        panel.grid.minor = element_blank(),
        panel.border=element_rect(fill=NA, 
                                  size=0.5,
                                  color ="black"))
  return(plot)
}

pdf("OGG_clusterBoxPlot.pdf")
boxAS(stageVark3AS90)
boxAS(stageVark4AS90)
boxAS(stageVark5AS90)
boxAS(stageVark6AS90)
boxAS(stageVark3AS)
boxAS(stageVark4AS)
boxAS(stageVark5AS)
boxAS(stageVark6AS)
dev.off()
