---
title: "MeanByCluster_OGG"
author: "Becca"
date: "December 8, 2016"
output: html_document
---

To compare rank correlations in gene expression across species at different time points (early, middle, late) we have to first collapse the within species variation to one score per OGG for each species,timestep(k). SpeciesClustmeanWI

```{r}
#a=Xlaev.interspecificNORM.avgOGG
#a1=Xlaev_clusterID
#k=3

library("dplyr")
library("plyr")
SpeciesClustmeanWI<-function(a, a1, k){
a1<-a1[,c(1,2,k)]
colnames(a1)=c("species", "timepoint", "k")
a=cbind.data.frame(a, timepoint=a1$timepoint)
ak=merge(a1, a, by='timepoint', all=FALSE)
ak=ak[,-c(1:2)]
ak1= plyr::ddply(data.frame(ak),  "k", plyr::numcolwise(mean))
ak1=ak1[,-1]
return(ak1)
}

SpeciesClustVarWI<-function(a, a1, k){
a1<-a1[,c(1,2,k)]
colnames(a1)=c("species", "timepoint", "k")
a=cbind.data.frame(a, timepoint=a1$timepoint)
ak=merge(a1, a, by='timepoint', all=FALSE)
ak=ak[,-c(1:2)]
ak1= plyr::ddply(data.frame(ak),  "k", plyr::numcolwise(var))
ak1=ak1[,-1]
return(ak1)
}
```
Implimentation of SpeciesClustmeanWI to average gene expression within cluster
```{r}
MusMeanBYclust3<-SpeciesClustmeanWI(Mus.shared.OGG.exp[-c(2:4),], 
                                    Mus_clusterID, 3)
GalMeanBYclust3<-SpeciesClustmeanWI(Gal.shared.OGG.exp, 
                                    Gallus_clusterID, 3)
DanMeanBYclust3<-SpeciesClustmeanWI(Dan.shared.OGG.exp[-c(1,12:15),], 
                                    Danio_clusterID, 3)
XlaevMeanBYclust3<-SpeciesClustmeanWI(Xlaev.shared.OGG.exp, 
                                      Xlaev_clusterID, 3)
XtropMeanBYclust3<-SpeciesClustmeanWI(Xtrop.shared.OGG.exp, 
                                      Xtrop_clusterID, 3)

MusMeanBYclust4<-SpeciesClustmeanWI(Mus.shared.OGG.exp[-c(2:4),], 
                                    Mus_clusterID, 4)
GalMeanBYclust4<-SpeciesClustmeanWI(Gal.shared.OGG.exp, 
                                    Gallus_clusterID, 4)
DanMeanBYclust4<-SpeciesClustmeanWI(Dan.shared.OGG.exp[-c(1,12:15),], 
                                    Danio_clusterID, 4)
XlaevMeanBYclust4<-SpeciesClustmeanWI(Xlaev.shared.OGG.exp, 
                                      Xlaev_clusterID, 4)
XtropMeanBYclust4<-SpeciesClustmeanWI(Xtrop.shared.OGG.exp, 
                                      Xtrop_clusterID, 4)

MusMeanBYclust5<-SpeciesClustmeanWI(Mus.shared.OGG.exp[-c(2:4),], 
                                    Mus_clusterID, 5)
GalMeanBYclust5<-SpeciesClustmeanWI(Gal.shared.OGG.exp, 
                                    Gallus_clusterID, 5)
DanMeanBYclust5<-SpeciesClustmeanWI(Dan.shared.OGG.exp[-c(1,12:15),], 
                                    Danio_clusterID, 5)
XlaevMeanBYclust5<-SpeciesClustmeanWI(Xlaev.shared.OGG.exp, 
                                      Xlaev_clusterID, 5)
XtropMeanBYclust5<-SpeciesClustmeanWI(Xtrop.shared.OGG.exp, 
                                      Xtrop_clusterID, 5)

####################################
MusMeanBYclust5var<-SpeciesClustVarWI(Mus.shared.OGG.exp[-c(2:4),], 
                                       Mus_clusterID, 5)
GalMeanBYclust5var<-SpeciesClustVarWI(Gal.shared.OGG.exp, 
                                       Gallus_clusterID, 5)
DanMeanBYclust5var<-SpeciesClustVarWI(Dan.shared.OGG.exp[-c(1,12:15),],
                                       Danio_clusterID, 5)
XlaevMeanBYclust5var<-SpeciesClustVarWI(Xlaev.shared.OGG.exp, 
                                         Xlaev_clusterID, 5)
XtropMeanBYclust5var<-SpeciesClustVarWI(Xtrop.shared.OGG.exp,
                                        Xtrop_clusterID, 5)

```

PWstageCor -- in AllPWcor.Rmd
```{r}
AllClustCor3<-rbind.data.frame(diag(PWstageCor(MusMeanBYclust3, GalMeanBYclust3)), 
                 diag(PWstageCor(MusMeanBYclust3, DanMeanBYclust3)),
                 diag(PWstageCor(MusMeanBYclust3, XlaevMeanBYclust3)),
                 diag(PWstageCor(MusMeanBYclust3, XtropMeanBYclust3)),
                 diag(PWstageCor(GalMeanBYclust3, DanMeanBYclust3)),
                 diag(PWstageCor(GalMeanBYclust3, XlaevMeanBYclust3)),
                 diag(PWstageCor(GalMeanBYclust3, XtropMeanBYclust3)),
                 diag(PWstageCor(DanMeanBYclust3, XlaevMeanBYclust3)),
                 diag(PWstageCor(DanMeanBYclust3, XtropMeanBYclust3)),
                 diag(PWstageCor(XtropMeanBYclust3, XlaevMeanBYclust3)))
colnames(AllClustCor3)<-c("cluster1", "cluster2", "cluster3")
rownames(AllClustCor3)<-c("MusGal", "MusDan", "MusXlaev", "MusXtrop", "GalDan",
                          "GalXlaev", "GalXtrop", "XlaevDan", "XtropDan", 
                          "XlaevXtrop")
AllClustCor3_Nolaevis<-AllClustCor3[-c(3,6,8,10),]
AllClustCor3_Notrop<-AllClustCor3[-c(4,7,9:10),]

AllClustCor4<-rbind.data.frame(diag(PWstageCor(MusMeanBYclust4, GalMeanBYclust4)), 
                 diag(PWstageCor(MusMeanBYclust4, DanMeanBYclust4)),
                 diag(PWstageCor(MusMeanBYclust4, XlaevMeanBYclust4)),
                 diag(PWstageCor(MusMeanBYclust4, XtropMeanBYclust4)),
                 diag(PWstageCor(GalMeanBYclust4, DanMeanBYclust4)),
                 diag(PWstageCor(GalMeanBYclust4, XlaevMeanBYclust4)),
                 diag(PWstageCor(GalMeanBYclust4, XtropMeanBYclust4)),
                 diag(PWstageCor(DanMeanBYclust4, XlaevMeanBYclust4)),
                 diag(PWstageCor(DanMeanBYclust4, XtropMeanBYclust4)),
                 diag(PWstageCor(XtropMeanBYclust4, XlaevMeanBYclust4)))
colnames(AllClustCor4)<-c("cluster1", "cluster2", "cluster3", "cluster4")
rownames(AllClustCor4)<-c("MusGal", "MusDan", "MusXlaev", "MusXtrop", "GalDan",
                          "GalXlaev", "GalXtrop", "XlaevDan", "XtropDan", 
                          "XlaevXtrop")
AllClustCor4_Nolaevis<-AllClustCor4[-c(3,6,8,10),]
AllClustCor4_Notrop<-AllClustCor4[-c(4,7,9:10),]


AllClustCor5<-rbind.data.frame(diag(PWstageCor(MusMeanBYclust5, GalMeanBYclust5)), 
                 diag(PWstageCor(MusMeanBYclust5, DanMeanBYclust5)),
                 diag(PWstageCor(MusMeanBYclust5, XlaevMeanBYclust5)),
                 diag(PWstageCor(MusMeanBYclust5, XtropMeanBYclust5)),
                 diag(PWstageCor(GalMeanBYclust5, DanMeanBYclust5)),
                 diag(PWstageCor(GalMeanBYclust5, XlaevMeanBYclust5)),
                 diag(PWstageCor(GalMeanBYclust5, XtropMeanBYclust5)),
                 diag(PWstageCor(DanMeanBYclust5, XlaevMeanBYclust5)),
                 diag(PWstageCor(DanMeanBYclust5, XtropMeanBYclust5)),
                 diag(PWstageCor(XtropMeanBYclust5, XlaevMeanBYclust5)))
colnames(AllClustCor5)<-c("cluster1", "cluster2", "cluster3", "cluster4", "cluster5")
rownames(AllClustCor5)<-c("MusGal", "MusDan", "MusXlaev", "MusXtrop", "GalDan",
                          "GalXlaev", "GalXtrop", "XlaevDan", "XtropDan", 
                          "XlaevXtrop")

AllClustCor5_Nolaevis<-AllClustCor5[-c(3,6,8,10),]
AllClustCor5_Notrop<-AllClustCor5[-c(4,7,9:10),]

#run all below to regenerate the peakedness 
AllClustCor5_Nolaevis_peakedness<-cbind.data.frame(colnames(AllClustCor5_Nolaevis),
                                                   apply(AllClustCor5_Nolaevis, 2, mean))
colnames(AllClustCor5_Nolaevis_peakedness)<-c("cluster", "clusterMean")
AllClustCor5_Nolaevis_peakedness<-cbind.data.frame(filter(AllClustCor5_Nolaevis_peakedness, 
                                                       cluster %in% c("cluster3", 
                                                                      "cluster2")) %>%
                                                     dplyr::summarise(uppermean = mean(clusterMean)),
                                                #second, filter, group and mean other non-peak clusters
                                                filter(AllClustCor5_Nolaevis_peakedness,
                                                       cluster %in% c("cluster1",
                                                                      "cluster4",
                                                                      "cluster5")) %>% 
                                                  dplyr::summarise(lowermean = mean(clusterMean))) 

AllClustCor5_Nolaevis_peakedness<-mutate(AllClustCor5_Nolaevis_peakedness, 
                                        peak = uppermean - lowermean)
  
```
Compare Clust correlation by phylogenetic relatedness
Implimentation of SpeciesClustmeanWI use the microarray data normalized for comparison accross species (see normalizeArrayBYsp.Rmd) Normalization takes the mean gene expression across all included time point and subtract that from the expression value. 
```{r, weird -- do not use... microarray values normalized for for across species comps}
MusMeanBYclust3_norm<-SpeciesClustmeanWI(Mus.interspecificNORM.avgOGG, Mus_clusterID, 3)
GalMeanBYclust3_norm<-SpeciesClustmeanWI(Gal.interspecificNORM.avgOGG, Gallus_clusterID, 3)
DanMeanBYclust3_norm<-SpeciesClustmeanWI(Dan.interspecificNORM.avgOGG, Danio_clusterID, 3)
XlaevMeanBYclust3_norm<-SpeciesClustmeanWI(Xlaev.interspecificNORM.avgOGG, Xlaev_clusterID, 3)
XtropMeanBYclust3_norm<-SpeciesClustmeanWI(Xtrop.interspecificNORM.avgOGG, Xtrop_clusterID, 3)

MusMeanBYclust4_norm<-SpeciesClustmeanWI(Mus.interspecificNORM.avgOGG, Mus_clusterID, 4)
GalMeanBYclust4_norm<-SpeciesClustmeanWI(Gal.interspecificNORM.avgOGG, Gallus_clusterID, 4)
DanMeanBYclust4_norm<-SpeciesClustmeanWI(Dan.interspecificNORM.avgOGG, Danio_clusterID, 4)
XlaevMeanBYclust4_norm<-SpeciesClustmeanWI(Xlaev.interspecificNORM.avgOGG, Xlaev_clusterID, 4)
XtropMeanBYclust4_norm<-SpeciesClustmeanWI(Xtrop.interspecificNORM.avgOGG, Xtrop_clusterID, 4)

MusMeanBYclust5_norm<-SpeciesClustmeanWI(Mus.interspecificNORM.avgOGG, Mus_clusterID, 5)
GalMeanBYclust5_norm<-SpeciesClustmeanWI(Gal.interspecificNORM.avgOGG, Gallus_clusterID, 5)
DanMeanBYclust5_norm<-SpeciesClustmeanWI(Dan.interspecificNORM.avgOGG, Danio_clusterID, 5)
XlaevMeanBYclust5_norm<-SpeciesClustmeanWI(Xlaev.interspecificNORM.avgOGG, Xlaev_clusterID, 5)
XtropMeanBYclust5_norm<-SpeciesClustmeanWI(Xtrop.interspecificNORM.avgOGG, Xtrop_clusterID, 5)

```
for the normalized data
PWstageCor -- in AllPWcor.Rmd
```{r--weird normalization}
AllClustCor3_norm<-rbind.data.frame(diag(PWstageCor(MusMeanBYclust3_norm, GalMeanBYclust3_norm)), 
                 diag(PWstageCor(MusMeanBYclust3_norm, DanMeanBYclust3_norm)),
                 diag(PWstageCor(MusMeanBYclust3_norm, XlaevMeanBYclust3_norm)),
                 diag(PWstageCor(MusMeanBYclust3_norm, XtropMeanBYclust3_norm)),
                 diag(PWstageCor(GalMeanBYclust3_norm, DanMeanBYclust3_norm)),
                 diag(PWstageCor(GalMeanBYclust3_norm, XlaevMeanBYclust3_norm)),
                 diag(PWstageCor(GalMeanBYclust3_norm, XtropMeanBYclust3_norm)),
                 diag(PWstageCor(DanMeanBYclust3_norm, XlaevMeanBYclust3_norm)),
                 diag(PWstageCor(DanMeanBYclust3_norm, XtropMeanBYclust3_norm)),
                 diag(PWstageCor(XtropMeanBYclust3_norm, XlaevMeanBYclust3_norm)))
colnames(AllClustCor3_norm)<-c("cluster1", "cluster2", "cluster3")
rownames(AllClustCor3_norm)<-c("MusGal", "MusDan", "MusXlaev", "MusXtrop", "GalDan",
                          "GalXlaev", "GalXtrop", "XlaevDan", "XtropDan", 
                          "XlaevXtrop")

AllClustCor4_norm<-rbind.data.frame(diag(PWstageCor(MusMeanBYclust4_norm, GalMeanBYclust4_norm)), 
                 diag(PWstageCor(MusMeanBYclust4_norm, DanMeanBYclust4_norm)),
                 diag(PWstageCor(MusMeanBYclust4_norm, XlaevMeanBYclust4_norm)),
                 diag(PWstageCor(MusMeanBYclust4_norm, XtropMeanBYclust4_norm)),
                 diag(PWstageCor(GalMeanBYclust4_norm, DanMeanBYclust4_norm)),
                 diag(PWstageCor(GalMeanBYclust4_norm, XlaevMeanBYclust4_norm)),
                 diag(PWstageCor(GalMeanBYclust4_norm, XtropMeanBYclust4_norm)),
                 diag(PWstageCor(DanMeanBYclust4_norm, XlaevMeanBYclust4_norm)),
                 diag(PWstageCor(DanMeanBYclust4_norm, XtropMeanBYclust4_norm)),
                 diag(PWstageCor(XtropMeanBYclust4_norm, XlaevMeanBYclust4_norm)))
colnames(AllClustCor4_norm)<-c("cluster1", "cluster2", "cluster3", "cluster4")
rownames(AllClustCor4_norm)<-c("MusGal", "MusDan", "MusXlaev", "MusXtrop", "GalDan",
                          "GalXlaev", "GalXtrop", "XlaevDan", "XtropDan", 
                          "XlaevXtrop")

AllClustCor5_norm<-rbind.data.frame(diag(PWstageCor(MusMeanBYclust5_norm, GalMeanBYclust5_norm)), 
                 diag(PWstageCor(MusMeanBYclust5_norm, DanMeanBYclust5_norm)),
                 diag(PWstageCor(MusMeanBYclust5_norm, XlaevMeanBYclust5_norm)),
                 diag(PWstageCor(MusMeanBYclust5_norm, XtropMeanBYclust5_norm)),
                 diag(PWstageCor(GalMeanBYclust5_norm, DanMeanBYclust5_norm)),
                 diag(PWstageCor(GalMeanBYclust5_norm, XlaevMeanBYclust5_norm)),
                 diag(PWstageCor(GalMeanBYclust5_norm, XtropMeanBYclust5_norm)),
                 diag(PWstageCor(DanMeanBYclust5_norm, XlaevMeanBYclust5_norm)),
                 diag(PWstageCor(DanMeanBYclust5_norm, XtropMeanBYclust5_norm)),
                 diag(PWstageCor(XtropMeanBYclust5_norm, XlaevMeanBYclust5_norm)))
colnames(AllClustCor5_norm)<-c("cluster1", "cluster2", "cluster3", "cluster4", "cluster5")
rownames(AllClustCor5_norm)<-c("MusGal", "MusDan", "MusXlaev", "MusXtrop", "GalDan",
                          "GalXlaev", "GalXtrop", "XlaevDan", "XtropDan", 
                          "XlaevXtrop")

```

check for hourglass

```{r}
library("reshape2")
library("ggplot2")
box_RankCor_clust<-function(x){
  rbind.data.frame(x, "cluster"=colnames(x))
  x=t(x)
  df<-melt(x, id="cluster")
  #df<-df[,-1]
  #colnames(df)<-c("k", "OGG", "acrossVar")
  #df$k<-as.factor(df$k)
  plot<-ggplot(df, aes(x=Var1, y=value))+
    geom_boxplot()+
    ylab("rank correlation")+  
    theme_bw() + 
    theme(axis.title.x=element_blank(),
        axis.text.x=element_text(size=18,face="plain", 
                                 color="black"),
        axis.text.y=element_text(size=14,
                                 face="plain"),
        axis.title.y=element_text(size=18,
                                  face="bold"),
        panel.grid.major=element_blank(),
        panel.grid.minor = element_blank(),
        panel.border=element_rect(fill=NA, 
                                  size=0.5,
                                  color ="black"))
  return(plot)
}

#x=AllClustCor5_Nolaevis
#not generating the smoothed area?
scatter_RankCor<-function(x){
  #x=rbind.data.frame(x, 
                  # "cluster"=colnames(x))
  x=t(x)
  df<-melt(x, id="cluster")
  plot=ggplot(df, 
         aes(x=as.factor(Var1), 
             y=value,
             color=Var2))+
    geom_point(shape = 1, lwd=5, stroke=1.5)+
    geom_smooth(method=x)+ #this isn't adding the ribbon
    ylab("rank correlation")+  
    theme_bw() + 
    theme(axis.title.x=element_blank(),
        axis.text.x=element_text(size=18,face="plain", 
                                 color="black"),
        axis.text.y=element_text(size=14,
                                 face="plain"),
        axis.title.y=element_text(size=18,
                                  face="bold"),
        panel.grid.major=element_blank(),
        panel.grid.minor = element_blank(),
        panel.border=element_rect(fill=NA, 
                                  size=0.5,
                                  color ="black"))
  return(plot)
}
```

```{r}
pdf("AllClustCor_NoXlXt.pdf", useDingbats = FALSE)
box_RankCor_clust(AllClustCor3[-10,])
box_RankCor_clust(AllClustCor4[-10,])
box_RankCor_clust(AllClustCor5[-10,])
dev.off()

pdf("AllClustCor.pdf", useDingbats = FALSE)
box_RankCor_clust(AllClustCor3)
box_RankCor_clust(AllClustCor4)
box_RankCor_clust(AllClustCor5)
dev.off()

pdf("AllClustCor_NoXlaevis.pdf", useDingbats = FALSE)
box_RankCor_clust(AllClustCor3[-c(4,9,10),])
box_RankCor_clust(AllClustCor4[-c(4,9,10),])
box_RankCor_clust(AllClustCor5[-c(4,9,10),])
dev.off()

pdf("AllClustCor_NoXtrop.pdf", useDingbats = FALSE)
box_RankCor_clust(AllClustCor3[-c(3,8,10),])
box_RankCor_clust(AllClustCor4[-c(3,8,10),])
box_RankCor_clust(AllClustCor5[-c(3,8,10),])
dev.off()


```

```{r}
x=AllClustCor3
y=nrow(x)
k1<-data.frame(x$k1)
colnames(k1)<-"k"
k2<-data.frame(x$k2)
colnames(k2)<-"k"
k3<-data.frame(x$k3)
colnames(k3)<-"k"
time<-data.frame(rep(c("k1",
                       "k2",
                       "k3"), 
                     c(y,
                       y,
                       y)))
k3all=cbind.data.frame(time,k)
colnames(k3all)<-c("time","k")

summary(aov(k~time, data=k3all))
TukeyHSD(aov(k~time, data=k3all))


x=AllClustCor4[-10,]
y=nrow(x)
k1<-data.frame(x$cluster1)
colnames(k1)<-"k"
k2<-data.frame(x$cluster2)
colnames(k2)<-"k"
k3<-data.frame(x$cluster3)
colnames(k3)<-"k"
k4<-data.frame(x$cluster4)
colnames(k4)<-"k"
k=rbind.data.frame(k1,k2,k3,k4)
time<-data.frame(rep(c("k1",
                       "k2",
                       "k3",
                       "k4"), 
                     c(y,
                       y,
                       y,
                       y)))
k4all=cbind.data.frame(time,k)
colnames(k4all)<-c("time","k")

summary(aov(k~time, data=k4all))
TukeyHSD(aov(k~time, data=k4all))

x=(AllClustCor5)
y=nrow(x)
k1<-data.frame(x$cluster1)
colnames(k1)<-"k"
k2<-data.frame(x$cluster2)
colnames(k2)<-"k"
k3<-data.frame(x$cluster3)
colnames(k3)<-"k"
k4<-data.frame(x$cluster4)
colnames(k4)<-"k"
k5<-data.frame(x$cluster5)
colnames(k5)<-"k"
k=rbind.data.frame(k1,
                   k2,
                   k3,
                   k4,
                   k5)
time<-data.frame(rep(c("k1",
                       "k2",
                       "k3",
                       "k4",
                       "k5"), 
                     c(y,
                       y,
                       y,
                       y,
                       y)))
k5all=cbind.data.frame(time,
                       k)
colnames(k5all)<-c("time",
                   "k")

summary(aov(k~time, 
            data=k5all))
TukeyHSD(aov(k~time, 
             data=k5all))

x=(AllClustCor5_Nolaevis)
y=nrow(x)
k1<-data.frame(x$cluster1)
colnames(k1)<-"k"
k2<-data.frame(x$cluster2)
colnames(k2)<-"k"
k3<-data.frame(x$cluster3)
colnames(k3)<-"k"
k4<-data.frame(x$cluster4)
colnames(k4)<-"k"
k5<-data.frame(x$cluster5)
colnames(k5)<-"k"
k=rbind.data.frame(k1,
                   k2,
                   k3,
                   k4,
                   k5)
time<-data.frame(rep(c("k1",
                       "k2",
                       "k3",
                       "k4",
                       "k5"), 
                     c(y,
                       y,
                       y,
                       y,
                       y)))
k5all=cbind.data.frame(time,
                       k)
colnames(k5all)<-c("time",
                   "k")

summary(aov(k~time, 
            data=k5all))
TukeyHSD(aov(k~time, 
             data=k5all))

x=(AllClustCor5_Notrop)
y=nrow(x)
k1<-data.frame(x$cluster1)
colnames(k1)<-"k"
k2<-data.frame(x$cluster2)
colnames(k2)<-"k"
k3<-data.frame(x$cluster3)
colnames(k3)<-"k"
k4<-data.frame(x$cluster4)
colnames(k4)<-"k"
k5<-data.frame(x$cluster5)
colnames(k5)<-"k"
k=rbind.data.frame(k1,
                   k2,
                   k3,
                   k4,
                   k5)
time<-data.frame(rep(c("k1",
                       "k2",
                       "k3",
                       "k4",
                       "k5"), 
                     c(y,
                       y,
                       y,
                       y,
                       y)))
k5all=cbind.data.frame(time,
                       k)
colnames(k5all)<-c("time",
                   "k")

summary(aov(k~time, 
            data=k5all))
TukeyHSD(aov(k~time, 
             data=k5all))

```

```{r}
Mus90MeanBYclust3<-SpeciesClustmeanWI(Mus.shareTime90, Mus_clusterID, 3)
Gal90MeanBYclust3<-SpeciesClustmeanWI(Gal.shareTime90, Gallus_clusterID, 3)
Dan90MeanBYclust3<-SpeciesClustmeanWI(Dan.shareTime90, Danio_clusterID, 3)
Xlaev90MeanBYclust3<-SpeciesClustmeanWI(Xlaev.shareTime90, Xlaev_clusterID, 3)
Xtrop90MeanBYclust3<-SpeciesClustmeanWI(Xtrop.shareTime90, Xtrop_clusterID, 3)

Mus90MeanBYclust4<-SpeciesClustmeanWI(Mus.shareTime90, Mus_clusterID, 4)
Gal90MeanBYclust4<-SpeciesClustmeanWI(Gal.shareTime90, Gallus_clusterID, 4)
Dan90MeanBYclust4<-SpeciesClustmeanWI(Dan.shareTime90, Danio_clusterID, 4)
Xlaev90MeanBYclust4<-SpeciesClustmeanWI(Xlaev.shareTime90, Xlaev_clusterID, 4)
Xtrop90MeanBYclust4<-SpeciesClustmeanWI(Xtrop.shareTime90, Xtrop_clusterID, 4)

Mus90MeanBYclust5<-SpeciesClustmeanWI(Mus.shareTime90, Mus_clusterID, 5)
Gal90MeanBYclust5<-SpeciesClustmeanWI(Gal.shareTime90, Gallus_clusterID, 5)
Dan90MeanBYclust5<-SpeciesClustmeanWI(Dan.shareTime90, Danio_clusterID, 5)
Xlaev90MeanBYclust5<-SpeciesClustmeanWI(Xlaev.shareTime90, Xlaev_clusterID, 5)
Xtrop90MeanBYclust5<-SpeciesClustmeanWI(Xtrop.shareTime90, Xtrop_clusterID, 5)

Mus90MeanBYclust6<-SpeciesClustmeanWI(Mus.shareTime90, Mus_clusterID, 6)
Gal90MeanBYclust6<-SpeciesClustmeanWI(Gal.shareTime90, Gallus_clusterID, 6)
Dan90MeanBYclust6<-SpeciesClustmeanWI(Dan.shareTime90, Danio_clusterID, 6)
Xlaev90MeanBYclust6<-SpeciesClustmeanWI(Xlaev.shareTime90, Xlaev_clusterID, 6)
Xtrop90MeanBYclust6<-SpeciesClustmeanWI(Xtrop.shareTime90, Xtrop_clusterID, 6)

Clust90Cor3<-rbind.data.frame(diag(PWstageCor(Mus90MeanBYclust3, Gal90MeanBYclust3)), 
                 diag(PWstageCor(Mus90MeanBYclust3, Dan90MeanBYclust3)),
                 diag(PWstageCor(Mus90MeanBYclust3, Xlaev90MeanBYclust3)),
                 diag(PWstageCor(Mus90MeanBYclust3, Xtrop90MeanBYclust3)),
                 diag(PWstageCor(Gal90MeanBYclust3, Dan90MeanBYclust3)),
                 diag(PWstageCor(Gal90MeanBYclust3, Xlaev90MeanBYclust3)),
                 diag(PWstageCor(Gal90MeanBYclust3, Xtrop90MeanBYclust3)),
                 diag(PWstageCor(Dan90MeanBYclust3, Xlaev90MeanBYclust3)),
                 diag(PWstageCor(Dan90MeanBYclust3, Xtrop90MeanBYclust3)),
                 diag(PWstageCor(Xtrop90MeanBYclust3, Xlaev90MeanBYclust3)))
colnames(Clust90Cor3)<-c("k1", "k2", "k3")

Clust90Cor4<-rbind.data.frame(diag(PWstageCor(Mus90MeanBYclust4, Gal90MeanBYclust4)), 
                 diag(PWstageCor(Mus90MeanBYclust4, Dan90MeanBYclust4)),
                 diag(PWstageCor(Mus90MeanBYclust4, Xlaev90MeanBYclust4)),
                 diag(PWstageCor(Mus90MeanBYclust4, Xtrop90MeanBYclust4)),
                 diag(PWstageCor(Gal90MeanBYclust4, Dan90MeanBYclust4)),
                 diag(PWstageCor(Gal90MeanBYclust4, Xlaev90MeanBYclust4)),
                 diag(PWstageCor(Gal90MeanBYclust4, Xtrop90MeanBYclust4)),
                 diag(PWstageCor(Dan90MeanBYclust4, Xlaev90MeanBYclust4)),
                 diag(PWstageCor(Dan90MeanBYclust4, Xtrop90MeanBYclust4)),
                 diag(PWstageCor(Xtrop90MeanBYclust4, Xlaev90MeanBYclust4)))
colnames(Clust90Cor4)<-c("k1", "k2", "k3", "k4")

Clust90Cor5<-rbind.data.frame(diag(PWstageCor(Mus90MeanBYclust5, Gal90MeanBYclust5)), 
                 diag(PWstageCor(Mus90MeanBYclust5, Dan90MeanBYclust5)),
                 diag(PWstageCor(Mus90MeanBYclust5, Xlaev90MeanBYclust5)),
                 diag(PWstageCor(Mus90MeanBYclust5, Xtrop90MeanBYclust5)),
                 diag(PWstageCor(Gal90MeanBYclust5, Dan90MeanBYclust5)),
                 diag(PWstageCor(Gal90MeanBYclust5, Xlaev90MeanBYclust5)),
                 diag(PWstageCor(Gal90MeanBYclust5, Xtrop90MeanBYclust5)),
                 diag(PWstageCor(Dan90MeanBYclust5, Xlaev90MeanBYclust5)),
                 diag(PWstageCor(Dan90MeanBYclust5, Xtrop90MeanBYclust5)),
                 diag(PWstageCor(Xtrop90MeanBYclust5, Xlaev90MeanBYclust5)))
colnames(Clust90Cor5)<-c("k1", "k2", "k3", "k4", "k5")

Clust90Cor6<-rbind.data.frame(diag(PWstageCor(Mus90MeanBYclust6, Gal90MeanBYclust6)), 
                 diag(PWstageCor(Mus90MeanBYclust6, Dan90MeanBYclust6)),
                 diag(PWstageCor(Mus90MeanBYclust6, Xlaev90MeanBYclust6)),
                 diag(PWstageCor(Mus90MeanBYclust6, Xtrop90MeanBYclust6)),
                 diag(PWstageCor(Gal90MeanBYclust6, Dan90MeanBYclust6)),
                 diag(PWstageCor(Gal90MeanBYclust6, Xlaev90MeanBYclust6)),
                 diag(PWstageCor(Gal90MeanBYclust6, Xtrop90MeanBYclust6)),
                 diag(PWstageCor(Dan90MeanBYclust6, Xlaev90MeanBYclust6)),
                 diag(PWstageCor(Dan90MeanBYclust6, Xtrop90MeanBYclust6)),
                 diag(PWstageCor(Xtrop90MeanBYclust6, Xlaev90MeanBYclust6)))
colnames(Clust90Cor6)<-c("k1", "k2", "k3", "k4", "k5", "k6")

```

```{r}

pdf("Cust90Cor.pdf", useDingbats = FALSE)
box_RankCor_clust(Clust90Cor3)
box_RankCor_clust(Clust90Cor4)
box_RankCor_clust(Clust90Cor5)
box_RankCor_clust(Clust90Cor6)
dev.off()
```

```{r}
x=Clust90Cor3
k1<-data.frame(x$k1)
colnames(k1)<-"k"
k2<-data.frame(x$k2)
colnames(k2)<-"k"
k3<-data.frame(x$k3)
colnames(k3)<-"k"
k=rbind.data.frame(k1,k2,k3)
time<-data.frame(rep(c("k1","k2","k3"), c(10,10,10)))
k3all=cbind.data.frame(time,k)
colnames(k3all)<-c("time","k")

summary(aov(k~time, data=k3all))
TukeyHSD(aov(k~time, data=k3all))


x=Clust90Cor4
k1<-data.frame(x$k1)
colnames(k1)<-"k"
k2<-data.frame(x$k2)
colnames(k2)<-"k"
k3<-data.frame(x$k3)
colnames(k3)<-"k"
k4<-data.frame(x$k4)
colnames(k4)<-"k"
k=rbind.data.frame(k1,k2,k3,k4)
time<-data.frame(rep(c("k1","k2","k3","k4"), c(10,10,10,10)))
k4all=cbind.data.frame(time,k)
colnames(k4all)<-c("time","k")

summary(aov(k~time, data=k4all))
TukeyHSD(aov(k~time, data=k4all))

x=Clust90Cor5
k1<-data.frame(x$k1)
colnames(k1)<-"k"
k2<-data.frame(x$k2)
colnames(k2)<-"k"
k3<-data.frame(x$k3)
colnames(k3)<-"k"
k4<-data.frame(x$k4)
colnames(k4)<-"k"
k5<-data.frame(x$k5)
colnames(k5)<-"k"
k=rbind.data.frame(k1,k2,k3,k4,k5)
time<-data.frame(rep(c("k1","k2","k3","k4","k5"), c(10,10,10,10,10)))
k5all=cbind.data.frame(time,k)
colnames(k5all)<-c("time","k")

summary(aov(k~time, data=k5all))
TukeyHSD(aov(k~time, data=k5all))

x=Clust90Cor6
k1<-data.frame(x$k1)
colnames(k1)<-"k"
k2<-data.frame(x$k2)
colnames(k2)<-"k"
k3<-data.frame(x$k3)
colnames(k3)<-"k"
k4<-data.frame(x$k4)
colnames(k4)<-"k"
k5<-data.frame(x$k5)
colnames(k5)<-"k"
k6<-data.frame(x$k6)
colnames(k6)<-"k"
k=rbind.data.frame(k1,k2,k3,k4,k5,k6)
time<-data.frame(rep(c("k1","k2","k3","k4","k5","k6"), c(10,10,10,10,10,10)))
k6all=cbind.data.frame(time,k)
colnames(k6all)<-c("time","k")

summary(aov(k~time, data=k6all))
TukeyHSD(aov(k~time, data=k6all))
```

```{r}
MusKeyMeanBYclust3<-SpeciesClustmeanWI(MusKeyDev.shared[c(1,5:19),], Mus_clusterID, 3)
GalKeyMeanBYclust3<-SpeciesClustmeanWI(GalKeyDev.shared, Gallus_clusterID, 3)
DanKeyMeanBYclust3<-SpeciesClustmeanWI(DanKeyDev.shared[-c(1,12:15),], Danio_clusterID, 3)
XlaevKeyMeanBYclust3<-SpeciesClustmeanWI(XlaevKeyDev.shared, Xlaev_clusterID, 3)
XtropKeyMeanBYclust3<-SpeciesClustmeanWI(Xtrop.shareTime90, Xtrop_clusterID, 3)

MusKeyMeanBYclust4<-SpeciesClustmeanWI(MusKeyDev.shared[c(1,5:19),], Mus_clusterID, 4)
GalKeyMeanBYclust4<-SpeciesClustmeanWI(GalKeyDev.shared, Gallus_clusterID, 4)
DanKeyMeanBYclust4<-SpeciesClustmeanWI(DanKeyDev.shared[-c(1,12:15),], Danio_clusterID, 4)
XlaevKeyMeanBYclust4<-SpeciesClustmeanWI(XlaevKeyDev.shared, Xlaev_clusterID, 4)
XtropKeyMeanBYclust4<-SpeciesClustmeanWI(XtropKeyDev.shared, Xtrop_clusterID, 4)

MusKeyMeanBYclust5<-SpeciesClustmeanWI(MusKeyDev.shared[c(1,5:19),], Mus_clusterID, 5)
GalKeyMeanBYclust5<-SpeciesClustmeanWI(GalKeyDev.shared, Gallus_clusterID, 5)
DanKeyMeanBYclust5<-SpeciesClustmeanWI(DanKeyDev.shared[-c(1,12:15),], Danio_clusterID, 5)
XlaevKeyMeanBYclust5<-SpeciesClustmeanWI(XlaevKeyDev.shared, Xlaev_clusterID, 5)
XtropKeyMeanBYclust5<-SpeciesClustmeanWI(XtropKeyDev.shared, Xtrop_clusterID, 5)

MusKeyMeanBYclust6<-SpeciesClustmeanWI(MusKeyDev.shared[c(1,5:19),], Mus_clusterID, 6)
GalKeyMeanBYclust6<-SpeciesClustmeanWI(GalKeyDev.shared, Gallus_clusterID, 6)
DanKeyMeanBYclust6<-SpeciesClustmeanWI(DanKeyDev.shared[-c(1,12:15),], Danio_clusterID, 6)
XlaevKeyMeanBYclust6<-SpeciesClustmeanWI(XlaevKeyDev.shared, Xlaev_clusterID, 6)
XtropKeyMeanBYclust6<-SpeciesClustmeanWI(XtropKeyDev.shared, Xtrop_clusterID, 6)
```

```{r}
ClustKeyCor3<-rbind.data.frame(diag(PWstageCor(MusKeyMeanBYclust3, GalKeyMeanBYclust3)), 
                 diag(PWstageCor(MusKeyMeanBYclust3, DanKeyMeanBYclust3)),
                 diag(PWstageCor(MusKeyMeanBYclust3, XlaevKeyMeanBYclust3)),
                 diag(PWstageCor(MusKeyMeanBYclust3, XtropKeyMeanBYclust3)),
                 diag(PWstageCor(GalKeyMeanBYclust3, DanKeyMeanBYclust3)),
                 diag(PWstageCor(GalKeyMeanBYclust3, XlaevKeyMeanBYclust3)),
                 diag(PWstageCor(GalKeyMeanBYclust3, XtropKeyMeanBYclust3)),
                 diag(PWstageCor(DanKeyMeanBYclust3, XlaevKeyMeanBYclust3)),
                 diag(PWstageCor(DanKeyMeanBYclust3, XtropKeyMeanBYclust3)),
                 diag(PWstageCor(XtropKeyMeanBYclust3, XlaevKeyMeanBYclust3)))
colnames(ClustKeyCor3)<-c("k1", "k2", "k3")

ClustKeyCor4<-rbind.data.frame(diag(PWstageCor(MusKeyMeanBYclust4, GalKeyMeanBYclust4)), 
                 diag(PWstageCor(MusKeyMeanBYclust4, DanKeyMeanBYclust4)),
                 diag(PWstageCor(MusKeyMeanBYclust4, XlaevKeyMeanBYclust4)),
                 diag(PWstageCor(MusKeyMeanBYclust4, XtropKeyMeanBYclust4)),
                 diag(PWstageCor(GalKeyMeanBYclust4, DanKeyMeanBYclust4)),
                 diag(PWstageCor(GalKeyMeanBYclust4, XlaevKeyMeanBYclust4)),
                 diag(PWstageCor(GalKeyMeanBYclust4, XtropKeyMeanBYclust4)),
                 diag(PWstageCor(DanKeyMeanBYclust4, XlaevKeyMeanBYclust4)),
                 diag(PWstageCor(DanKeyMeanBYclust4, XtropKeyMeanBYclust4)),
                 diag(PWstageCor(XtropKeyMeanBYclust4, XlaevKeyMeanBYclust4)))
colnames(Clust90Cor4)<-c("k1", "k2", "k3", "k4")

ClustKeyCor5<-rbind.data.frame(diag(PWstageCor(MusKeyMeanBYclust5, GalKeyMeanBYclust5)), 
                 diag(PWstageCor(MusKeyMeanBYclust5, DanKeyMeanBYclust5)),
                 diag(PWstageCor(MusKeyMeanBYclust5, XlaevKeyMeanBYclust5)),
                 diag(PWstageCor(MusKeyMeanBYclust5, XtropKeyMeanBYclust5)),
                 diag(PWstageCor(GalKeyMeanBYclust5, DanKeyMeanBYclust5)),
                 diag(PWstageCor(GalKeyMeanBYclust5, XlaevKeyMeanBYclust5)),
                 diag(PWstageCor(GalKeyMeanBYclust5, XtropKeyMeanBYclust5)),
                 diag(PWstageCor(DanKeyMeanBYclust5, XlaevKeyMeanBYclust5)),
                 diag(PWstageCor(DanKeyMeanBYclust5, XtropKeyMeanBYclust5)),
                 diag(PWstageCor(XtropKeyMeanBYclust5, XlaevKeyMeanBYclust5)))
colnames(Clust90Cor5)<-c("k1", "k2", "k3", "k4", "k5")

ClustKeyCor6<-rbind.data.frame(diag(PWstageCor(MusKeyMeanBYclust6, GalKeyMeanBYclust6)), 
                 diag(PWstageCor(MusKeyMeanBYclust6, DanKeyMeanBYclust6)),
                 diag(PWstageCor(MusKeyMeanBYclust6, XlaevKeyMeanBYclust6)),
                 diag(PWstageCor(MusKeyMeanBYclust6, XtropKeyMeanBYclust6)),
                 diag(PWstageCor(GalKeyMeanBYclust6, DanKeyMeanBYclust6)),
                 diag(PWstageCor(GalKeyMeanBYclust6, XlaevKeyMeanBYclust6)),
                 diag(PWstageCor(GalKeyMeanBYclust6, XtropKeyMeanBYclust6)),
                 diag(PWstageCor(DanKeyMeanBYclust6, XlaevKeyMeanBYclust6)),
                 diag(PWstageCor(DanKeyMeanBYclust6, XtropKeyMeanBYclust6)),
                 diag(PWstageCor(XtropKeyMeanBYclust6, XlaevKeyMeanBYclust6)))
colnames(Clust90Cor6)<-c("k1", "k2", "k3", "k4", "k5", "k6")
```

```{r}
pdf("Cust90Cor.pdf", useDingbats = FALSE)
box_RankCor_clust(ClustKeyCor3)
box_RankCor_clust(ClustKeyCor4)
box_RankCor_clust(ClustKeyCor5)
box_RankCor_clust(ClustKeyCor6)
dev.off()
```


```{r}
library("plyr")
#caluclates the within species mean of each OGG for k clusters
stageClustmeanWI<-function(a, a1, b, b1, c, c1, 
                        d, d1, e, e1, k, spA, 
                        spB, spC, spD, spE){
a1<-a1[,c(1,2,k+1)]
colnames(a1)=c("species", "timepoint", "k")
a=cbind.data.frame(a, timepoint=row.names(a))
ak=merge(a1, a, by='timepoint', all=FALSE)
ak=ak[,-c(1:2)]
ak1= ddply(data.frame(ak),  "k", numcolwise(mean))
ak1<-cbind.data.frame(ak1, "species"=rep(spA, k))
ak1=ak1[,c(ncol(ak1),1:ncol(ak1)-1)]

b1<-b1[,c(1,2,k+1)]
colnames(b1)=c("species", "timepoint", "k")
b=cbind.data.frame(b, timepoint=row.names(b))
bk=merge(b1, b,by='timepoint', all=FALSE)
bk=bk[,-c(1:2)]
bk1= ddply(data.frame(bk),  "k", numcolwise(mean))
bk1<-cbind.data.frame(bk1, "species"=rep(spB, k))
bk1=bk1[,c(ncol(bk1),1:ncol(bk1)-1)]

c1<-c1[,c(1,2,k+1)]
colnames(c1)=c("species", "timepoint", "k")
c=cbind.data.frame(c, timepoint=row.names(c))
ck=merge(c1, c,by='timepoint', all=FALSE)
ck=ck[,-c(1:2)]
ck1= ddply(data.frame(ck),  "k", numcolwise(mean))
ck1<-cbind.data.frame(ck1, "species"=rep(spC, k))
ck1=ck1[,c(ncol(ck1),1:ncol(ck1)-1)]

d1=d1[,c(1,2,k+1)]
colnames(d1)=c("species", "timepoint", "k")
d=cbind.data.frame(d, timepoint=d1$timepoint)
dk=merge(d1, d,by='timepoint', all=FALSE)
dk=dk[,-c(1:2)]
dk1= ddply(data.frame(dk),  "k", numcolwise(mean))
dk1<-cbind.data.frame(dk1, "species"=rep(spD, k))
dk1=dk1[,c(ncol(dk1),1:ncol(dk1)-1)]

e1=e1[,c(1,2,k+1)]
colnames(e1)=c("species", "timepoint", "k")
e=cbind.data.frame(e, timepoint=e1$timepoint)
ek=merge(e1, e,by='timepoint', all=FALSE)
ek=ek[,-c(1:2)]
ek1= ddply((ek),  "k", numcolwise(mean))
ek1<-cbind.data.frame(ek1, "species"=rep(spE, k))
ek1=ek1[,c(ncol(ek1),1:ncol(ek1)-1)]

all=rbind.data.frame(ak1, bk1, ck1, dk1, ek1)
return(all)
}

```

```{r}
stageMean3WI<-stageClustmeanWI(Mus.shared.OGG.exp, Mus_clusterID, 
                                             Gal.shared.OGG.exp, Gallus_clusterID,
                                             Dan.shared.OGG.exp, Danio_clusterID, 
                                             Xlaev.shared.OGG.exp, Xlaev_clusterID, 
                                             Xtrop.shared.OGG.exp, Xtrop_clusterID, 
                                             3, "Mus", "Gallus", "Danio", "Xlaev", "Xtrop")

stageMean4WI<-stageClustmeanWI(Mus.shared.OGG.exp, Mus_clusterID, 
                                             Gal.shared.OGG.exp, Gallus_clusterID,
                                             Dan.shared.OGG.exp, Danio_clusterID, 
                                             Xlaev.shared.OGG.exp, Xlaev_clusterID, 
                                             Xtrop.shared.OGG.exp, Xtrop_clusterID, 
                                             4, "Mus", "Gallus", "Danio", "Xlaev", "Xtrop")

stageMean5WI<-stageClustmeanWI(Mus.shared.OGG.exp, Mus_clusterID, 
                                             Gal.shared.OGG.exp, Gallus_clusterID,
                                             Dan.shared.OGG.exp, Danio_clusterID, 
                                             Xlaev.shared.OGG.exp, Xlaev_clusterID, 
                                             Xtrop.shared.OGG.exp, Xtrop_clusterID, 
                                             5, "Mus", "Gallus", "Danio", "Xlaev", "Xtrop")

stageMean6WI<-stageClustmeanWI(Mus.shared.OGG.exp, Mus_clusterID, 
                                             Gal.shared.OGG.exp, Gallus_clusterID,
                                             Dan.shared.OGG.exp, Danio_clusterID, 
                                             Xlaev.shared.OGG.exp, Xlaev_clusterID, 
                                             Xtrop.shared.OGG.exp, Xtrop_clusterID, 
                                             6, "Mus", "Gallus", "Danio", "Xlaev", "Xtrop")
```