---
title: "MeanByCluster_OGG"
author: "Becca"
date: "December 8, 2016"
output: html_document
---

This markdown takes means by 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

To compare rank correlations in gene expression across species at different time points (early, middle, late) we have to first collapse the within species variation to one score per OGG for each species,timestep(k). SpeciesClustmeanWI

```{r}
#a=Xlaev.interspecificNORM.avgOGG
#a1=Xlaev_clusterID
#k=3

library("dplyr")
library("plyr")
SpeciesClustmeanWI<-function(a, a1, k){
a1<-a1[,c(1,2,k)]
colnames(a1)=c("species", "timepoint", "k")
a=cbind.data.frame(a, timepoint=a1$timepoint)
ak=merge(a1, a, by='timepoint', all=FALSE)
ak=ak[,-c(1:2)]
ak1= plyr::ddply(data.frame(ak),  "k", plyr::numcolwise(mean))
ak1=ak1[,-1]
return(ak1)
}

SpeciesClustVarWI<-function(a, a1, k){
a1<-a1[,c(1,2,k)]
colnames(a1)=c("species", "timepoint", "k")
a=cbind.data.frame(a, timepoint=a1$timepoint)
ak=merge(a1, a, by='timepoint', all=FALSE)
ak=ak[,-c(1:2)]
ak1= plyr::ddply(data.frame(ak),  "k", plyr::numcolwise(var))
ak1=ak1[,-1]
return(ak1)
}
```
Implimentation of SpeciesClustmeanWI to average gene expression within cluster
```{r}
MusMeanBYclust3<-SpeciesClustmeanWI(Mus.shared.OGG.exp[-c(2:4),], 
                                    Mus_clusterID, 3)
GalMeanBYclust3<-SpeciesClustmeanWI(Gal.shared.OGG.exp, 
                                    Gallus_clusterID, 3)
DanMeanBYclust3<-SpeciesClustmeanWI(Dan.shared.OGG.exp[-c(1,12:15),], 
                                    Danio_clusterID, 3)
XlaevMeanBYclust3<-SpeciesClustmeanWI(Xlaev.shared.OGG.exp, 
                                      Xlaev_clusterID, 3)
XtropMeanBYclust3<-SpeciesClustmeanWI(Xtrop.shared.OGG.exp, 
                                      Xtrop_clusterID, 3)

MusMeanBYclust4<-SpeciesClustmeanWI(Mus.shared.OGG.exp[-c(2:4),], 
                                    Mus_clusterID, 4)
GalMeanBYclust4<-SpeciesClustmeanWI(Gal.shared.OGG.exp, 
                                    Gallus_clusterID, 4)
DanMeanBYclust4<-SpeciesClustmeanWI(Dan.shared.OGG.exp[-c(1,12:15),], 
                                    Danio_clusterID, 4)
XlaevMeanBYclust4<-SpeciesClustmeanWI(Xlaev.shared.OGG.exp, 
                                      Xlaev_clusterID, 4)
XtropMeanBYclust4<-SpeciesClustmeanWI(Xtrop.shared.OGG.exp, 
                                      Xtrop_clusterID, 4)

MusMeanBYclust5<-SpeciesClustmeanWI(Mus.shared.OGG.exp[-c(2:4),], 
                                    Mus_clusterID, 5)
GalMeanBYclust5<-SpeciesClustmeanWI(Gal.shared.OGG.exp, 
                                    Gallus_clusterID, 5)
DanMeanBYclust5<-SpeciesClustmeanWI(Dan.shared.OGG.exp[-c(1,12:15),], 
                                    Danio_clusterID, 5)
XlaevMeanBYclust5<-SpeciesClustmeanWI(Xlaev.shared.OGG.exp, 
                                      Xlaev_clusterID, 5)
XtropMeanBYclust5<-SpeciesClustmeanWI(Xtrop.shared.OGG.exp, 
                                      Xtrop_clusterID, 5)

```

PWstageCor -- in AllPWcor.Rmd
```{r}
AllClustCor3<-rbind.data.frame(diag(PWstageCor(MusMeanBYclust3, GalMeanBYclust3)), 
                 diag(PWstageCor(MusMeanBYclust3, DanMeanBYclust3)),
                 diag(PWstageCor(MusMeanBYclust3, XlaevMeanBYclust3)),
                 diag(PWstageCor(MusMeanBYclust3, XtropMeanBYclust3)),
                 diag(PWstageCor(GalMeanBYclust3, DanMeanBYclust3)),
                 diag(PWstageCor(GalMeanBYclust3, XlaevMeanBYclust3)),
                 diag(PWstageCor(GalMeanBYclust3, XtropMeanBYclust3)),
                 diag(PWstageCor(DanMeanBYclust3, XlaevMeanBYclust3)),
                 diag(PWstageCor(DanMeanBYclust3, XtropMeanBYclust3)),
                 diag(PWstageCor(XtropMeanBYclust3, XlaevMeanBYclust3)))
colnames(AllClustCor3)<-c("cluster1", "cluster2", "cluster3")
rownames(AllClustCor3)<-c("MusGal", "MusDan", "MusXlaev", "MusXtrop", "GalDan",
                          "GalXlaev", "GalXtrop", "XlaevDan", "XtropDan", 
                          "XlaevXtrop")
AllClustCor3_Nolaevis<-AllClustCor3[-c(3,6,8,10),]
AllClustCor3_Notrop<-AllClustCor3[-c(4,7,9:10),]

AllClustCor4<-rbind.data.frame(diag(PWstageCor(MusMeanBYclust4, GalMeanBYclust4)), 
                 diag(PWstageCor(MusMeanBYclust4, DanMeanBYclust4)),
                 diag(PWstageCor(MusMeanBYclust4, XlaevMeanBYclust4)),
                 diag(PWstageCor(MusMeanBYclust4, XtropMeanBYclust4)),
                 diag(PWstageCor(GalMeanBYclust4, DanMeanBYclust4)),
                 diag(PWstageCor(GalMeanBYclust4, XlaevMeanBYclust4)),
                 diag(PWstageCor(GalMeanBYclust4, XtropMeanBYclust4)),
                 diag(PWstageCor(DanMeanBYclust4, XlaevMeanBYclust4)),
                 diag(PWstageCor(DanMeanBYclust4, XtropMeanBYclust4)),
                 diag(PWstageCor(XtropMeanBYclust4, XlaevMeanBYclust4)))
colnames(AllClustCor4)<-c("cluster1", "cluster2", "cluster3", "cluster4")
rownames(AllClustCor4)<-c("MusGal", "MusDan", "MusXlaev", "MusXtrop", "GalDan",
                          "GalXlaev", "GalXtrop", "XlaevDan", "XtropDan", 
                          "XlaevXtrop")
AllClustCor4_Nolaevis<-AllClustCor4[-c(3,6,8,10),]
AllClustCor4_Notrop<-AllClustCor4[-c(4,7,9:10),]


AllClustCor5<-rbind.data.frame(diag(PWstageCor(MusMeanBYclust5, GalMeanBYclust5)), 
                 diag(PWstageCor(MusMeanBYclust5, DanMeanBYclust5)),
                 diag(PWstageCor(MusMeanBYclust5, XlaevMeanBYclust5)),
                 diag(PWstageCor(MusMeanBYclust5, XtropMeanBYclust5)),
                 diag(PWstageCor(GalMeanBYclust5, DanMeanBYclust5)),
                 diag(PWstageCor(GalMeanBYclust5, XlaevMeanBYclust5)),
                 diag(PWstageCor(GalMeanBYclust5, XtropMeanBYclust5)),
                 diag(PWstageCor(DanMeanBYclust5, XlaevMeanBYclust5)),
                 diag(PWstageCor(DanMeanBYclust5, XtropMeanBYclust5)),
                 diag(PWstageCor(XtropMeanBYclust5, XlaevMeanBYclust5)))
colnames(AllClustCor5)<-c("cluster1", "cluster2", "cluster3", "cluster4", "cluster5")
rownames(AllClustCor5)<-c("MusGal", "MusDan", "MusXlaev", "MusXtrop", "GalDan",
                          "GalXlaev", "GalXtrop", "XlaevDan", "XtropDan", 
                          "XlaevXtrop")

AllClustCor5_Nolaevis<-AllClustCor5[-c(3,6,8,10),]
AllClustCor5_Notrop<-AllClustCor5[-c(4,7,9:10),]

#run all below to regenerate the peakedness 
AllClustCor5_Nolaevis_peakedness<-cbind.data.frame(colnames(AllClustCor5_Nolaevis),
                                                   apply(AllClustCor5_Nolaevis, 2, mean))
colnames(AllClustCor5_Nolaevis_peakedness)<-c("cluster", "clusterMean")
AllClustCor5_Nolaevis_peakedness<-cbind.data.frame(filter(AllClustCor5_Nolaevis_peakedness, 
                                                       cluster %in% c("cluster3", 
                                                                      "cluster2")) %>%
                                                     dplyr::summarise(uppermean = mean(clusterMean)),
                                                #second, filter, group and mean other non-peak clusters
                                                filter(AllClustCor5_Nolaevis_peakedness,
                                                       cluster %in% c("cluster1",
                                                                      "cluster4",
                                                                      "cluster5")) %>% 
                                                  dplyr::summarise(lowermean = mean(clusterMean))) 

AllClustCor5_Nolaevis_peakedness<-mutate(AllClustCor5_Nolaevis_peakedness, 
                                        peak = uppermean - lowermean)
  
```

check for hourglass

```{r}
library("reshape2")
library("ggplot2")
box_RankCor_clust<-function(x){
  rbind.data.frame(x, "cluster"=colnames(x))
  x=t(x)
  df<-melt(x, id="cluster")
  #df<-df[,-1]
  #colnames(df)<-c("k", "OGG", "acrossVar")
  #df$k<-as.factor(df$k)
  plot<-ggplot(df, aes(x=Var1, y=value))+
    geom_boxplot()+
    ylab("rank correlation")+  
    theme_bw() + 
    theme(axis.title.x=element_blank(),
        axis.text.x=element_text(size=18,face="plain", 
                                 color="black"),
        axis.text.y=element_text(size=14,
                                 face="plain"),
        axis.title.y=element_text(size=18,
                                  face="bold"),
        panel.grid.major=element_blank(),
        panel.grid.minor = element_blank(),
        panel.border=element_rect(fill=NA, 
                                  size=0.5,
                                  color ="black"))
  return(plot)
}

#x=AllClustCor5_Nolaevis
#not generating the smoothed area?
scatter_RankCor<-function(x){
  #x=rbind.data.frame(x, 
                  # "cluster"=colnames(x))
  x=t(x)
  df<-melt(x, id="cluster")
  plot=ggplot(df, 
         aes(x=as.factor(Var1), 
             y=value,
             color=Var2))+
    geom_point(shape = 1, lwd=5, stroke=1.5)+
    geom_smooth(method=x)+ #this isn't adding the ribbon
    ylab("rank correlation")+  
    theme_bw() + 
    theme(axis.title.x=element_blank(),
        axis.text.x=element_text(size=18,face="plain", 
                                 color="black"),
        axis.text.y=element_text(size=14,
                                 face="plain"),
        axis.title.y=element_text(size=18,
                                  face="bold"),
        panel.grid.major=element_blank(),
        panel.grid.minor = element_blank(),
        panel.border=element_rect(fill=NA, 
                                  size=0.5,
                                  color ="black"))
  return(plot)
}
```

```{r}
pdf("AllClustCor_NoXlXt.pdf", useDingbats = FALSE)
box_RankCor_clust(AllClustCor3[-10,])
box_RankCor_clust(AllClustCor4[-10,])
box_RankCor_clust(AllClustCor5[-10,])
dev.off()

pdf("AllClustCor.pdf", useDingbats = FALSE)
box_RankCor_clust(AllClustCor3)
box_RankCor_clust(AllClustCor4)
box_RankCor_clust(AllClustCor5)
dev.off()

pdf("AllClustCor_NoXlaevis.pdf", useDingbats = FALSE)
box_RankCor_clust(AllClustCor3[-c(4,9,10),])
box_RankCor_clust(AllClustCor4[-c(4,9,10),])
box_RankCor_clust(AllClustCor5[-c(4,9,10),])
dev.off()

pdf("AllClustCor_NoXtrop.pdf", useDingbats = FALSE)
box_RankCor_clust(AllClustCor3[-c(3,8,10),])
box_RankCor_clust(AllClustCor4[-c(3,8,10),])
box_RankCor_clust(AllClustCor5[-c(3,8,10),])
dev.off()


```

```{r}
x=AllClustCor3
y=nrow(x)
k1<-data.frame(x$k1)
colnames(k1)<-"k"
k2<-data.frame(x$k2)
colnames(k2)<-"k"
k3<-data.frame(x$k3)
colnames(k3)<-"k"
time<-data.frame(rep(c("k1",
                       "k2",
                       "k3"), 
                     c(y,
                       y,
                       y)))
k3all=cbind.data.frame(time,k)
colnames(k3all)<-c("time","k")

summary(aov(k~time, data=k3all))
TukeyHSD(aov(k~time, data=k3all))


x=AllClustCor4[-10,]
y=nrow(x)
k1<-data.frame(x$cluster1)
colnames(k1)<-"k"
k2<-data.frame(x$cluster2)
colnames(k2)<-"k"
k3<-data.frame(x$cluster3)
colnames(k3)<-"k"
k4<-data.frame(x$cluster4)
colnames(k4)<-"k"
k=rbind.data.frame(k1,k2,k3,k4)
time<-data.frame(rep(c("k1",
                       "k2",
                       "k3",
                       "k4"), 
                     c(y,
                       y,
                       y,
                       y)))
k4all=cbind.data.frame(time,k)
colnames(k4all)<-c("time","k")

summary(aov(k~time, data=k4all))
TukeyHSD(aov(k~time, data=k4all))

x=(AllClustCor5)
y=nrow(x)
k1<-data.frame(x$cluster1)
colnames(k1)<-"k"
k2<-data.frame(x$cluster2)
colnames(k2)<-"k"
k3<-data.frame(x$cluster3)
colnames(k3)<-"k"
k4<-data.frame(x$cluster4)
colnames(k4)<-"k"
k5<-data.frame(x$cluster5)
colnames(k5)<-"k"
k=rbind.data.frame(k1,
                   k2,
                   k3,
                   k4,
                   k5)
time<-data.frame(rep(c("k1",
                       "k2",
                       "k3",
                       "k4",
                       "k5"), 
                     c(y,
                       y,
                       y,
                       y,
                       y)))
k5all=cbind.data.frame(time,
                       k)
colnames(k5all)<-c("time",
                   "k")

summary(aov(k~time, 
            data=k5all))
TukeyHSD(aov(k~time, 
             data=k5all))

x=(AllClustCor5_Nolaevis)
y=nrow(x)
k1<-data.frame(x$cluster1)
colnames(k1)<-"k"
k2<-data.frame(x$cluster2)
colnames(k2)<-"k"
k3<-data.frame(x$cluster3)
colnames(k3)<-"k"
k4<-data.frame(x$cluster4)
colnames(k4)<-"k"
k5<-data.frame(x$cluster5)
colnames(k5)<-"k"
k=rbind.data.frame(k1,
                   k2,
                   k3,
                   k4,
                   k5)
time<-data.frame(rep(c("k1",
                       "k2",
                       "k3",
                       "k4",
                       "k5"), 
                     c(y,
                       y,
                       y,
                       y,
                       y)))
k5all=cbind.data.frame(time,
                       k)
colnames(k5all)<-c("time",
                   "k")

summary(aov(k~time, 
            data=k5all))
TukeyHSD(aov(k~time, 
             data=k5all))

x=(AllClustCor5_Notrop)
y=nrow(x)
k1<-data.frame(x$cluster1)
colnames(k1)<-"k"
k2<-data.frame(x$cluster2)
colnames(k2)<-"k"
k3<-data.frame(x$cluster3)
colnames(k3)<-"k"
k4<-data.frame(x$cluster4)
colnames(k4)<-"k"
k5<-data.frame(x$cluster5)
colnames(k5)<-"k"
k=rbind.data.frame(k1,
                   k2,
                   k3,
                   k4,
                   k5)
time<-data.frame(rep(c("k1",
                       "k2",
                       "k3",
                       "k4",
                       "k5"), 
                     c(y,
                       y,
                       y,
                       y,
                       y)))
k5all=cbind.data.frame(time,
                       k)
colnames(k5all)<-c("time",
                   "k")

summary(aov(k~time, 
            data=k5all))
TukeyHSD(aov(k~time, 
             data=k5all))

```

