---
title: "IndependentContrasts"
author: "Becca"
date: "May 16, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This R Markdown document is meant to develop independent contrast approach to analyzing the interspecific microarray data through embryogenesis -- to investigate whether an hourglass in gene expression similarity is present. Attempting two approaches. One is at the OGG level (1), the second is at the phylogenetic node level (2). I am not as keen on (2), even more averaging!

(1)abs(OGG by cluster RANK #sp1ornode1 - OGG by cluster RANK #sp2 or node2)/sum(branch lengths)
NOTES: species OGG expression mean by cluster comes from:
\All_projects\Phylotypic Stage\R\PhylotypicStage\MeanByCluster_OGG.Rmd

```{r, establishing datasets for pairwise comparisons}
#generate species by cluster RANKs for all OGGs
# "-" on the matrix gives descending order, highest rank lowest expression
MusOGGRank_clust5<-data.frame(t(apply(-MusMeanBYclust5, 1, rank))) 
GalOGGRank_clust5<-data.frame(t(apply(-GalMeanBYclust5, 1, rank))) 
XlaevOGGRank_clust5<-data.frame(t(apply(-XlaevMeanBYclust5, 1, rank))) 
XtropOGGRank_clust5<-data.frame(t(apply(-XtropMeanBYclust5, 1, rank))) 
DanOGGRank_clust5<-data.frame(t(apply(-DanMeanBYclust5, 1, rank))) 

#For each node look at the difference in OGG rank correct by summed branch lengths:
#abs(RANKsp1-RANKsp2)/(branch length 1 + branch length 2)
#branch length are median time estimates from time tree. 
AmnioteOGGRank_contrast_clust5<-(abs(MusOGGRank_clust5 - 
                          GalOGGRank_clust5))/sqrt(320+320)
FrogOGGRank_contrast_clust5<-(abs(XlaevOGGRank_clust5 - 
                       XtropOGGRank_clust5))/sqrt(52+52)

AnamnioteOGGRank_contrast_clust5<-(abs((MusOGGRank_clust5/2 + 
                                GalOGGRank_clust5/2) - 
                              (XlaevOGGRank_clust5/2 + 
                                 XtropOGGRank_clust5/2))/
                                sqrt(35+301))

VertebrateOGGRank_contrast_clust5<-(abs((MusOGGRank_clust5/4 + 
                                GalOGGRank_clust5/4 + 
                                XlaevOGGRank_clust5/4 + 
                                 XtropOGGRank_clust5/4) -
                                 DanOGGRank_clust5)/
                                  sqrt(79+432))
```


```{r}

```
## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
