---
title: "GenerateOGG_expdata"
author: "Becca"
date: "Thursday, May 26, 2016"
output: pdf_document
---
Takes time-point x gene (row x col) expression data 'expr_data' and averages expression of genes in the 
same OGG using a conversion data frame 'OGG_data'. The 'OGG_data' argument takes a data frame with OGG IDs in column 1 and gene IDs in column 2. This function assumes many:1 mapping (no genes map to multiple OGGs)

```{r}
avgParalogousGenes <- function (expr_data, OGG_data) {
  
  ## Initialize output data frame
  new_data <- data.frame(
                matrix(data = vector(),
                       nrow = nrow(expr_data), 
                       ncol = 0), 
                stringsAsFactors=F)
  rownames(new_data) <- rownames(expr_data)
    
  ## Eliminate genes not mapped to an OGG
  ## if (!all(genes_in_OGG %in% colnames(expr_data))) {browser()}
  #expr_data <- expr_data[,colnames(expr_data) %in% as.character(OGG_data[,2])]
  OGG_data <- OGG_data[as.character(OGG_data[,2]) %in% colnames(expr_data), ]
  
  ## For each OGG, find all genes that map to it and append their average expression to the output
  for (OGG in unique(OGG_data[,1])) {
    genes_in_OGG <- as.character(OGG_data[,2][(OGG_data[,1] == OGG)])
    if (length(genes_in_OGG) == 1) {
     ##if (!genes_in_OGG %in% colnames(expr_data)) {browser()}
      new_data[,OGG] <- expr_data[,genes_in_OGG]
    } else {
      ##browser()
      ##if (!all(genes_in_OGG %in% colnames(expr_data))) {browser()}
      new_data[,OGG] <- rowMeans(expr_data[,genes_in_OGG])
    }
  }
  
  ## Return the output
  return(new_data)
}
```

Generate species specific OGG average expression datasets 
```{r}
Dan.sp.OGG.exp<-avgParalogousGenes(drer.all.stages,Dan.OGG)
Gal.sp.OGG.exp<-avgParalogousGenes(ggal.all.stages,Gal.OGG)
Mus.sp.OGG.exp<-avgParalogousGenes(mmus.all.stages.3,Mus.OGG)
Xlaev.sp.OGG.exp<-avgParalogousGenes(xlaev.all.stages,xlaev.OGG)
Xtrop.sp.OGG.exp<-avgParalogousGenes(xtrop.all.stages,xtrop.OGG)
```

cull the OGGs for each species to only contain those OGG for which expression data is available. Input Species mean expression by OGG (e.g., Gal.sp.OGG.exp)
```{r}
OGGs_with_expr_values<-function(OGG_data,expr_data) {
  new_data <- OGG_data[as.character(OGG_data[,1]) %in% colnames(expr_data), ]
  new_data <-as.character(new_data$OrthoGroup)
  ## Return the output
  return(new_data)
}
```

OGGs with available expression data in each species
```{r}
Dan.OGG.expressed<-OGGs_with_expr_values(Dan.OGG,Dan.sp.OGG.exp)
Gal.OGG.expressed<-OGGs_with_expr_values(Gal.OGG,Gal.sp.OGG.exp)
Mus.OGG.expressed<-OGGs_with_expr_values(Mus.OGG,Mus.sp.OGG.exp)
xlaev.OGG.expressed<-OGGs_with_expr_values(xlaev.OGG,Xlaev.sp.OGG.exp)
xtrop.OGG.expressed<-OGGs_with_expr_values(xtrop.OGG,Xtrop.sp.OGG.exp)

list.of.sp.OGGs<-list(Dan.OGG.expressed,Gal.OGG.expressed,Mus.OGG.expressed,xlaev.OGG.expressed,xtrop.OGG.expressed)

shared_OGGs<-Reduce(intersect,list.of.sp.OGGs)
```


Function to limit species level expression dataset to only include shared OGGs
```{r}
exprSharedOGGs <- function (OGGs, OGG_expr_sp) {
  ## Initialize output data frame
  new_data <- data.frame(
                matrix(data = vector(),
                       nrow = nrow(OGG_expr_sp), 
                       ncol = 0), 
                stringsAsFactors=F)
  rownames(new_data) <- rownames(OGG_expr_sp)
    
  ## Eliminate OGGs without expression data
  new_data <- OGG_expr_sp[,colnames(OGG_expr_sp) %in% OGGs]
  
  ## Return the output
  return(new_data)
}
```


Generate WORKING DATA including mean expression (across paralogs) for OGGs shared by all species
```{r}
###Critical to check the order of stages!
Dan.shared.OGG.exp<-exprSharedOGGs(shared_OGGs,Dan.sp.OGG.exp)
Gal.shared.OGG.exp<-exprSharedOGGs(shared_OGGs,Gal.sp.OGG.exp)
Mus.shared.OGG.exp<-exprSharedOGGs(shared_OGGs,Mus.sp.OGG.exp)
Xlaev.shared.OGG.exp<-exprSharedOGGs(shared_OGGs,Xlaev.sp.OGG.exp)
Xtrop.shared.OGG.exp<-exprSharedOGGs(shared_OGGs,Xtrop.sp.OGG.exp)
```

