---
title: "OGGselection_CV_FC"
author: "Becca"
date: "Wednesday, November 30, 2016"
output: html_document
---

This markdown contains code to identify OGGs that are interesting in embryogenesis. The metrics are: 
max(|log2FC|)/percent of development

max(|log2FC|) -- this is sensitive to inconsistent time steps (perhaps accounting for percent of development)
cum(|log2FC|) -- may be sensitive to noise (but this is less problematic in OGGs as compaired to genes)
CV -- this is time independent

Note: need to remove 1 cell stage from mouse and danio (maternal transcripts) and any data 5 days or later in danio (outside of embryogenesis)

```{r}
library("plyr")
library("dplyr")
#may want to do this by cluster?
#keep this in to test code as it is written
#x=MusMeanBYclust5 
#y=Mus_clusterID_time
#k=5
#p = 0.25 #percentage we want to select
OGG_FCbyPercentDevo<- function (x,y,k,p) {
  datalen=length(x[,1])
  ratios<-x[1:datalen-1,]/x[2:datalen,]
  ratios<-apply(ratios, 
                c(1, 2), 
                function(f) log(f,2))
  clusNum=max(y[,k+2])
  names<-paste(rep("clusterRatio", clusNum), 1:clusNum)
  clusterRatio=names[1:clusNum-1]
  row.names(ratios)<-clusterRatio
  #focus=paste("k.",k, sep="")
  percentTime = plyr::ddply(y, 
                            .(k.5), 
                            plyr::summarize, 
                            meanPercent=mean(PercentTime))
  percentTime<-percentTime[2:k,]-percentTime[1:k-1,]
  percentTime<-percentTime[,2]
  ratios<-apply(ratios, 2, function (q) q/percentTime)
  #IMPORTANT: the value is no longer correct, could be abs! 
  #This is just for selecting OGG with high max|FC|
  maxFC<-data.frame(apply(ratios, 2, function (x) { (max(abs(x)))}))
  colnames(maxFC)<-"maxFC"
  maxFC<-cbind.data.frame(maxFC, OGG=row.names(maxFC))
  #top p%
  selected <-data.frame(maxFC[c(maxFC$maxFC >= quantile(maxFC$maxFC, probs = p):2),])
  colnames(selected)<-c("max|log2FC|/%time", "OGG")
  return(selected)
}
```

```{r}
library("plyr")
library("dplyr")
#may want to do this by cluster?
#keep this in to test code as it is written
#x=MusMeanBYclust5 
#y=Mus_clusterID_time
#k=5
#p = 0.25 #percentage we want to select
OGG_FCbyPercentDevo<- function (x,y,k,p) {
  datalen=length(x[,1])
  ratios<-x[1:datalen-1,]/x[2:datalen,]
  ratios<-apply(ratios, 
                c(1, 2), 
                function(f) log(f,2))
  clusNum=max(y[,k+2])
  names<-paste(rep("clusterRatio", clusNum), 1:clusNum)
  clusterRatio=names[1:clusNum-1]
  row.names(ratios)<-clusterRatio
  #focus=paste("k.",k, sep="")
  percentTime = plyr::ddply(y, 
                            .(k.5), 
                            plyr::summarize, 
                            meanPercent=mean(PercentTime))
  percentTime<-percentTime[2:k,]-percentTime[1:k-1,]
  percentTime<-percentTime[,2]
  ratios<-apply(ratios, 2, function (q) q/percentTime)
  #IMPORTANT: the value is no longer correct, could be abs! 
  #This is just for selecting OGG with high max|FC|
  maxFC<-data.frame(apply(ratios, 2, function (x) { (max(abs(x)))}))
  colnames(maxFC)<-"maxFC"
  maxFC<-cbind.data.frame(maxFC, OGG=row.names(maxFC))
  #top p%
  selected <-data.frame(maxFC[c(maxFC$maxFC >= quantile(maxFC$maxFC, probs = p):2),])
  colnames(selected)<-c("max|log2FC|/%time", "OGG")
  return(selected)
}
```
```{r}
#x=Gal.shared.OGG.exp #keep this in to test code as it is written
#p = percentage we want to select
OGG_maxFC<- function (x,p) {
  datalen=length(x[,1])
  ratios<-as.matrix(log(x[1:datalen-1,]/x[2:datalen,]),2)
  names<-paste(rep("step", datalen), 1:datalen)
  steps=names[1:datalen-1]
  row.names(ratios)<-steps
  #IMPORTANT: the value is no longer correct, could be abs! 
  #This is just for selecting OGG with high max|FC|
  maxFC<-data.frame(apply(ratios, 2, function (x) { (max(abs(x)))}))
  colnames(maxFC)<-"maxFC"
  maxFC<-cbind.data.frame(maxFC, OGG=row.names(maxFC))
  #top p%
  selected <-data.frame(maxFC[c(maxFC$maxFC >= quantile(maxFC$maxFC, probs = p):2),])
  colnames(selected)<-c("max|log2FC|", "OGG")
  y<-t(x)
  y<-cbind.data.frame(y, OGG=row.names(y))
  MaxFC_selected<-merge(y,selected, by="OGG")
  row.names(MaxFC_selected)<-MaxFC_selected$OGG #put OGG names back as row names
  MaxFC_selected<-MaxFC_selected[,-c(datalen+2)] #remove the OGG name column and the max|logFC| columns 
  return(MaxFC_selected)
  }

OGG_cumFC<- function (x,p) {
  datalen=length(x[,1])
  ratios<-as.matrix(log(x[1:datalen-1,]/x[2:datalen,]),2)
  names<-paste(rep("step", datalen), 1:datalen)
  steps=names[1:datalen-1]
  row.names(ratios)<-steps
  #IMPORTANT: the value is no longer correct, could be abs! 
  #This is just for selecting OGG with high max|FC|
  cumFC<-data.frame(apply(ratios, 2, function (x) { (sum(abs(x)))}))
  colnames(cumFC)<-"cumFC"
  cumFC<-cbind.data.frame(cumFC, OGG=row.names(cumFC))
  #top p%
  selected <-data.frame(cumFC[c(cumFC$cumFC >= quantile(cumFC$cumFC, probs = p):2),])
  colnames(selected)<-c("cum|log2FC|", "OGG")
  y<-t(x)
  y<-cbind.data.frame(y, OGG=row.names(y))
  CumFC_selected<-merge(y,selected, by="OGG")
  row.names(CumFC_selected)<-CumFC_selected$OGG #put OGG names back as row names
  CumFC_selected<-CumFC_selected[,-c(datalen+2)] #remove the OGG name column and the max|logFC| columns
  return(CumFC_selected)
  }

OGG_CV<- function (x,p) {
  datalen=length(x[,1])
  z<-t(x)
  CV<-cbind.data.frame(z, CV=apply(z,1, function (y) var(y)/mean(y)))
  selected <-data.frame(CV[c(CV$CV >= quantile(CV$CV, probs = .9):2),])
  CV_selected=selected[,-c(datalen+1)]
  CV_selected=cbind.data.frame(CV_selected,
                               OGG=row.names(CV_selected))
  CV_selected=CV_selected[,c(ncol(CV_selected),
                             1:ncol(CV_selected)-1)]
  return(CV_selected)
  }
```

Implement the above, and merge among list within species. Remove 1cell stage in mus and danio and 5 days and after in danio
```{r}
Mus_MaxFC_PercentDev_OGG<-OGG_FCbyPercentDevo(MusMeanBYclust5, Mus_clusterID_time, 5, .9) #only works for k=5 right now
Gal_MaxFC_PercentDev_OGG<-OGG_FCbyPercentDevo(GalMeanBYclust5, Gallus_clusterID_time, 5, .9) #only works 
Xlaev_MaxFC_PercentDev_OGG<-OGG_FCbyPercentDevo(XlaevMeanBYclust5, Xlaev_clusterID_time, 5, .9) #only works 
Xtrop_MaxFC_PercentDev_OGG<-OGG_FCbyPercentDevo(XtropMeanBYclust5, Xtrop_clusterID_time, 5, .9) #only 
Dan_MaxFC_PercentDev_OGG<-OGG_FCbyPercentDevo(DanMeanBYclust5, Danio_clusterID_time, 5, .9) #only 

All_MaxFC_PercentDev<-Reduce(function(dtf1, dtf2) merge(dtf1, 
                                                        dtf2, 
                                                        by = "OGG", 
                                                        all = TRUE),
                             list(Mus_MaxFC_PercentDev_OGG,
                                  Gal_MaxFC_PercentDev_OGG, 
                                  Xlaev_MaxFC_PercentDev_OGG, 
                                  Xtrop_MaxFC_PercentDev_OGG,
                                  Dan_MaxFC_PercentDev_OGG))

All_MaxFC_PercentDev<-All_MaxFC_PercentDev[,1]

Mus_MaxFC_PercentDev_OGG<-Mus.shared.OGG.exp[All_MaxFC_PercentDev]
Mus_MaxFC_PercentDev_OGG<-Mus_MaxFC_PercentDev_OGG[c(1,5:19),]
Gal_MaxFC_PercentDev_OGG<-Gal.shared.OGG.exp[All_MaxFC_PercentDev]
Xlaev_MaxFC_PercentDev_OGG<-Xlaev.shared.OGG.exp[All_MaxFC_PercentDev]
Xtrop_MaxFC_PercentDev_OGG<-Xtrop.shared.OGG.exp[All_MaxFC_PercentDev]
Dan_MaxFC_PercentDev_OGG<-Dan.shared.OGG.exp[All_MaxFC_PercentDev]
Dan_MaxFC_PercentDev_OGG<-Dan_MaxFC_PercentDev_OGG[2:11,]

```
The following analysis uses functions from MeanByCluster_OGG.Rmd
```{r}
MusMeanBYclust5_MaxFC_PercentDev<-SpeciesClustmeanWI(Mus_MaxFC_PercentDev_OGG,
                                                     Mus_clusterID, 5)
GalMeanBYclust5_MaxFC_PercentDev<-SpeciesClustmeanWI(Gal_MaxFC_PercentDev_OGG,
                                                     Gallus_clusterID, 5)
DanMeanBYclust5_MaxFC_PercentDev<-SpeciesClustmeanWI(Dan_MaxFC_PercentDev_OGG,
                                                     Danio_clusterID, 5)
XlaevMeanBYclust5_MaxFC_PercentDev<-SpeciesClustmeanWI(Xlaev_MaxFC_PercentDev_OGG,
                                                       Xlaev_clusterID, 5)
XtropMeanBYclust5_MaxFC_PercentDev<-SpeciesClustmeanWI(Xtrop_MaxFC_PercentDev_OGG,
                                                       Xtrop_clusterID, 5)


AllClustCor5_MaxFC_PercentDev<-rbind.data.frame(diag(
  PWstageCor(MusMeanBYclust5_MaxFC_PercentDev,
             GalMeanBYclust5_MaxFC_PercentDev)), 
                 diag(PWstageCor(MusMeanBYclust5_MaxFC_PercentDev,
                                 DanMeanBYclust5_MaxFC_PercentDev)),
                 diag(PWstageCor(MusMeanBYclust5_MaxFC_PercentDev,
                                 XlaevMeanBYclust5_MaxFC_PercentDev)),
                 diag(PWstageCor(MusMeanBYclust5_MaxFC_PercentDev,
                                 XtropMeanBYclust5_MaxFC_PercentDev)),
                 diag(PWstageCor(GalMeanBYclust5_MaxFC_PercentDev,
                                 DanMeanBYclust5_MaxFC_PercentDev)),
                 diag(PWstageCor(GalMeanBYclust5_MaxFC_PercentDev,
                                 XlaevMeanBYclust5_MaxFC_PercentDev)),
                 diag(PWstageCor(GalMeanBYclust5_MaxFC_PercentDev,
                                 XtropMeanBYclust5_MaxFC_PercentDev)),
                 diag(PWstageCor(DanMeanBYclust5_MaxFC_PercentDev,
                                 XlaevMeanBYclust5_MaxFC_PercentDev)),
                 diag(PWstageCor(DanMeanBYclust5_MaxFC_PercentDev,
                                 XtropMeanBYclust5_MaxFC_PercentDev)),
                 diag(PWstageCor(XtropMeanBYclust5_MaxFC_PercentDev,
                                 XlaevMeanBYclust5_MaxFC_PercentDev)))
colnames(AllClustCor5_MaxFC_PercentDev)<-c("cluster1", 
                                           "cluster2", 
                                           "cluster3", 
                                           "cluster4", 
                                           "cluster5")
rownames(AllClustCor5_MaxFC_PercentDev)<-c("MusGal", 
                                           "MusDan", 
                                           "MusXlaev", 
                                           "MusXtrop", 
                                           "GalDan",
                                           "GalXlaev", 
                                           "GalXtrop", 
                                           "XlaevDan", 
                                           "XtropDan", 
                                           "XlaevXtrop")

AllClustCor5_MaxFC_PercentDev_Nolaevis<-AllClustCor5_MaxFC_PercentDev[-c(3,6,8,10),]
AllClustCor5_MaxFC_PercentDev_Notrop<-AllClustCor5_MaxFC_PercentDev[-c(4,7,9:10),]

library("reshape2")
library("ggplot2")
box_RankCor_clust(AllClustCor5_MaxFC_PercentDev_Nolaevis)
box_RankCor_clust(AllClustCor5_MaxFC_PercentDev_Notrop)
box_RankCor_clust(AllClustCor5_MaxFC_PercentDev)
```

CV and fold change Rmarkdown
```{r}
Mus_MaxFC_OGG<-OGG_maxFC(Mus.shared.OGG.exp[c(1,5:19),], .9)
Mus_CumFC_OGG<-OGG_cumFC(Mus.shared.OGG.exp[c(1,5:19),], .9)
Mus_CV_OGG<-OGG_CV(Mus.shared.OGG.exp[c(1,5:19),], .9)

Gal_MaxFC_OGG<-OGG_maxFC(Gal.shared.OGG.exp, .9)
Gal_CumFC_OGG<-OGG_cumFC(Gal.shared.OGG.exp, .9)
Gal_CV_OGG<-OGG_CV(Gal.shared.OGG.exp, .9)

Xlaev_CV_OGG<-OGG_CV(Xlaev.shared.OGG.exp, .9)
Xlaev_MaxFC_OGG<-OGG_maxFC(Xlaev.shared.OGG.exp, .9)
colnames(Xlaev_MaxFC_OGG)<-colnames(Xlaev_CV_OGG)
Xlaev_CumFC_OGG<-OGG_cumFC(Xlaev.shared.OGG.exp, .9)
colnames(Xlaev_CumFC_OGG)<-colnames(Xlaev_CV_OGG)

Xtrop_CV_OGG<-OGG_CV(Xtrop.shared.OGG.exp, .9)
Xtrop_MaxFC_OGG<-OGG_maxFC(Xtrop.shared.OGG.exp, .9)
colnames(Xtrop_MaxFC_OGG)<-colnames(Xtrop_CV_OGG)
Xtrop_CumFC_OGG<-OGG_cumFC(Xtrop.shared.OGG.exp, .9)
colnames(Xtrop_CumFC_OGG)<-colnames(Xtrop_CV_OGG)

Dan_CV_OGG<-OGG_CV(Dan.shared.OGG.exp[2:11,], .9)
Dan_MaxFC_OGG<-OGG_maxFC(Dan.shared.OGG.exp[2:11,], .9)
colnames(Dan_MaxFC_OGG)<-colnames(Dan_CV_OGG)
Dan_CumFC_OGG<-OGG_cumFC(Dan.shared.OGG.exp[2:11,], .9)
colnames(Dan_CumFC_OGG)<-colnames(Dan_CV_OGG)

```

funtion that merges the output from max, cum, CV analysis to get the robust list of time genes
```{r}
TimeOGGsp = function(x,y,z,sp) {
  combo=Reduce(function(x,y) {merge(x,y, all=TRUE)}, 
              list(x, y, z))
  row.names(combo)=combo$OGG
  datalen=length(combo[,1])
  #combo<-cbind.data.frame(combo, species=rep(sp,datalen))
  all<-combo[,c(ncol(combo),1:ncol(combo)-1)]
  #all=all[,-1]
  #all=t(all)
  return(combo)
}

Mus_TimeOGG<-TimeOGGsp(Mus_MaxFC_OGG,Mus_CumFC_OGG,Mus_CV_OGG, "mus")  
Gal_TimeOGG<-TimeOGGsp(Gal_MaxFC_OGG,Gal_CumFC_OGG,Gal_CV_OGG, "gallus")  
Xlaev_TimeOGG<-TimeOGGsp(Xlaev_MaxFC_OGG,Xlaev_CumFC_OGG,Xlaev_CV_OGG, "Xlaev") 
Xtrop_TimeOGG<-TimeOGGsp(Xtrop_MaxFC_OGG,Xtrop_CumFC_OGG,Xtrop_CV_OGG, "Xtrop")
Dan_TimeOGG<-TimeOGGsp(Dan_MaxFC_OGG,Dan_CumFC_OGG,Dan_CV_OGG, "danio")

All_TimeOGG90<-Reduce(function(x,y) {merge(x,y, by='OGG', all=FALSE)}, 
              list(Mus_TimeOGG, Gal_TimeOGG, 
                   Xlaev_TimeOGG,Xtrop_TimeOGG,
                   Dan_TimeOGG))

All_TimeOGG90_ID<-as.data.frame(All_TimeOGG90$OGG)
colnames(All_TimeOGG90_ID)<-"OGG"

Mus.shareTime90<-merge(Mus_TimeOGG, All_TimeOGG90_ID, by="OGG", keep=FALSE)
row.names(Mus.shareTime90)<-Mus.shareTime90$OGG
Mus.shareTime90<-t(Mus.shareTime90[,-1])

Gal.shareTime90<-merge(Gal_TimeOGG, All_TimeOGG90_ID, by="OGG", keep=FALSE)
row.names(Gal.shareTime90)<-Gal.shareTime90$OGG
Gal.shareTime90<-t(Gal.shareTime90[,-1])

Dan.shareTime90<-merge(Dan_TimeOGG, All_TimeOGG90_ID, by="OGG", keep=FALSE)
row.names(Dan.shareTime90)<-Dan.shareTime90$OGG
Dan.shareTime90<-t(Dan.shareTime90[,-1])

Xlaev.shareTime90<-merge(Xlaev_TimeOGG, All_TimeOGG90_ID, by="OGG", keep=FALSE)
row.names(Xlaev.shareTime90)<-Xlaev.shareTime90$OGG
Xlaev.shareTime90<-t(Xlaev.shareTime90[,-1])

Xtrop.shareTime90<-merge(Xtrop_TimeOGG, All_TimeOGG90_ID, by="OGG", keep=FALSE)
row.names(Xtrop.shareTime90)<-Xtrop.shareTime90$OGG
Xtrop.shareTime90<-t(Xtrop.shareTime90[,-1])



All_TimeOGG90incl<-Reduce(function(x,y) {merge(x,y, by='OGG', all=TRUE)}, 
              list(Mus_TimeOGG, Gal_TimeOGG, 
                   Xlaev_TimeOGG,Xtrop_TimeOGG,
                   Dan_TimeOGG))

```
Plot the 10 ten of each or the combined. 
```{r}
library("ggplot2")
library("reshape2")

#x=t(Mus_CV_OGG[,-1])
plot_topPercent<- function (x,nOGGs) {
  datalen=length(x[,1])
  ratios<-as.matrix(log(x[1:datalen-1,]/x[2:datalen,]),2)
  names<-paste(rep("step", datalen), 1:datalen)
  steps=names[1:datalen-1]
  ratios<-data.frame(ratios[,sample(ncol(ratios),nOGGs)])
  ratios<-t(ratios)
  ratios<-cbind.data.frame(ratios, OGGs=row.names(ratios))
  colnames(ratios)<-c(steps, 'OGGs')
  levels(ratios)<-steps
    ratios<-melt(ratios, id="OGGs")
  colnames(ratios)<-c("OGGs", "steps", "Log2dExp")
  y<-ggplot(ratios, aes(x = steps, y = Log2dExp, color=OGGs, group=OGGs)) +
    geom_path() +
    geom_point(size=2) +
    scale_y_continuous(limits = c(-.75, .75)) +
    theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(), 
    legend.position='none')
  return(y)}

plot_topPercent(t(Mus_CV_OGG[,-1]))
plot_topPercent(t(Mus_MaxFC_OGG[,-1]))
plot_topPercent(t(Mus_CumFC_OGG[,-1]))

plot_topPercent_exp<- function (x,nOGGs) {
  #datalen=length(x[,1])
  #ratios<-as.matrix(log(x[1:datalen-1,]/x[2:datalen,]),2)
  #names<-paste(rep("step", datalen), 1:datalen)
  steps=colnames(x[-1])
  #ratios<-data.frame(ratios[,sample(ncol(ratios),nOGGs)])
  #ratios<-t(ratios)
  #ratios<-cbind.data.frame(ratios, OGGs=row.names(ratios))
  #colnames(ratios)<-c(steps, 'OGGs')
  x<-melt(x, id="OGG")
  levels(x)<-steps
  colnames(x)<-c("OGGs", "stage", "Expression")
  y<-ggplot(x, aes(x = stage, y = Expression, color=OGGs, group=OGGs)) +
    geom_path() +
    geom_point(size=2) +
    scale_y_continuous(limits = c(0, 15)) +
    theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(), 
    legend.position='none')
  return(y)}





```
kmeans genes and plot
```{r}
x=Mus_MaxFC_OGG
k=10
#find the 'elbow' best number of k's
plot_koptimum<- function (mydata,k,z) {
  sp=z
  wss <- (nrow(mydata)-1)*sum(apply(mydata,2,var))
  for (i in 2:k) wss[i] <- sum(kmeans(mydata,
                                       centers=i)$withinss)
  y<-plot(1:k, wss, type="b", main=sp, xlab="Number of Clusters",
     ylab="Within groups sum of squares")
  return(y)}


plot_kmeansALLOGG_Exp<- function (x,k) {
  kclusters=kmeans(t(x),k)
  numbers=kclusters$size
  cluster.centers=t(data.frame(kclusters$center))
  stages=row.names(x)
  cluster.centers<-melt(cluster.centers, id="cluster")
  colnames(cluster.centers)<-c("stage","cluster", "Expression")
  cluster.centers$cluster<-as.factor(cluster.centers$cluster)
  levels(cluster.centers$stage)<-stages
  y<-ggplot(cluster.centers, 
            aes(x = stage, y = Expression, 
                color=cluster, group=cluster)) +
    geom_path(size=2)+ 
    geom_point(size=4) +
    scale_y_continuous(limits = c(2, 15)) +
    theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(), 
    legend.position='none')
    return(y)}


plot_kmeansOGG_Exp<- function (x,k) {
  kclusters=kmeans(x,k)
  cluster.centers=t(data.frame(kclusters$center))
  stages=x[,-1]
  cluster.centers<-melt(cluster.centers, id="cluster")
  colnames(cluster.centers)<-c("stage","cluster", "Expression")
  cluster.centers$cluster<-as.factor(cluster.centers$cluster)
  levels(cluster.centers$stage)<-stages
  y<-ggplot(cluster.centers, 
            aes(x = stage, y = Expression, color=cluster, group=cluster)) +
    geom_path(size=2)+ 
    geom_point(size=4) +
    scale_y_continuous(limits = c(2, 12)) +
    theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(), 
    legend.position='none')
    return(y)}

plot_koptimum(t(Gal.shared.OGG.exp),15,"Gallus")
plot_kmeansALLOGG_Exp(Gal.shared.OGG.exp,10)

plot_koptimum(Gal_CV_OGG[,-1],15,"Gallus")
plot_kmeansOGG_Exp(Gal_CV_OGG[,-1],10)

plot_koptimum(Gal_MaxFC_OGG[,-1],15,"Gallus")
plot_kmeansOGG_Exp(Gal_MaxFC_OGG[,-1],10)

plot_koptimum(Gal_CumFC_OGG[,-1],15,"Gallus")
plot_kmeansOGG_Exp(Gal_CumFC_OGG[,-1],10)

plot_koptimum(Mus_CV_OGG[,-1],15,"Mus")
plot_kmeansOGG_Exp(Mus_CV_OGG[,-1],10)

plot_koptimum(Mus_MaxFC_OGG[,-1],15,"Mus")
plot_kmeansOGG_Exp(Mus_MaxFC_OGG[,-1],10)

plot_koptimum(Mus_CumFC_OGG[,-1],15,"Mus")
plot_kmeansOGG_Exp(Mus_CumFC_OGG[,-1],10)

#plot_koptimum(Dan_CV_OGG[,-1],12,"Danio")
#plot_kmeansOGG_Exp(Dan_CV_OGG[,-1],7)

#plot_koptimum(Dan_MaxFC_OGG[,-1],12,"Danio")
#plot_kmeansOGG_Exp(Dan_MaxFC_OGG[,-1],7)

#plot_koptimum(Dan_CumFC_OGG[,-1],12,"Danio")
#plot_kmeansOGG_Exp(Dan_CumFC_OGG[,-1],7)





#kmeans of ratios (not as informative)
plot_kmeansOGG<- function (x,k) {
  kclusters=kmeans(x[,-1],k)
  cluster.centers=t(data.frame(kclusters$center))
  datalen=length(cluster.centers[,1])
  ratios<-as.matrix(log(cluster.centers[1:datalen-1,]/cluster.centers[2:datalen,]),2)
  names<-paste(rep("step", datalen), 1:datalen)
  steps=names[1:datalen-1]
  ratios<-t(ratios)
  ratios<-cbind.data.frame(ratios, cluster=row.names(ratios))
  colnames(ratios)<-c(steps, 'cluster')
  levels(ratios)<-steps
    ratios<-melt(ratios, id="cluster")
  colnames(ratios)<-c("cluster", "steps", "Log2dExp")
  y<-ggplot(ratios, aes(x = steps, 
                        y = Log2dExp, 
                        color=cluster, 
                        group=cluster)) +
    geom_path() +
    geom_point(size=2) +
    scale_y_continuous(limits = c(-.5, .5)) +
    theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(), 
    legend.position='none')
  return(y)}






```

