---
title: "PCA-Hourglass"
author: "Becca"
date: "Tuesday, June 07, 2016"
output: html_document
---

Generate a data set of all OGGs and run prcomp
OGG files have expression vales for each OGG, at each embyonic stage. Different files are different species
```{r}
#requires that the columns are in the same order!
All.shared.OGG.exp<-do.call("rbind", list(Dan.shared.OGG.exp, Gal.shared.OGG.exp, Mus.shared.OGG.exp, Xlaev.shared.OGG.exp, Xtrop.shared.OGG.exp))
  
All_PCA<-prcomp(All.shared.OGG.exp) 
All_PCs<-All_PCA$x
sp<-(as.data.frame(rep(c("Danio", "Gallus", "Mus", "X.laevis", "X.tropicalis"), c(15,15,19,15,15))))
colnames(sp)<-"sp"
#All_PCs<-cbind(sp, All_PCs)
summary(All_PCA)

TimeStep<-(as.data.frame(rep(c(-1, 0, 1, -1, 0, 1,-1, 0, 1,-1, 0, 1,-1, 0, 1), c(6,3,6,5,5,5,4,11,4,4,7,4,4,7,4))))
colnames(TimeStep)<-"time"
#All_PCs<-cbind(sp, TimeStep, All_PCs)

TimeRank<-c(c(1:15), c(1:15), c(1:19), c(1:15), c(1:15))
TimeRank<-as.data.frame(TimeRank)
colnames(TimeRank)<-"timeRank"
All_PCs<-cbind(sp, TimeStep, TimeRank, All_PCs)
summary(All_PCs)
All_PCloadings<-All_PCA$rotation

```

Perfom an ordinal logistic regression: PCs ~ TimeSteps using polr{MASS}

```{r}
#determine which PCs to include in downstream analysis. Must explain >1% of the variation (arbitraty cut. )
summary(All_PCA)

library("MASS")
TimeStepPC_OLR=polr(factor(time) ~ PC1 + PC2 + PC3 + PC4 + PC5 + PC6, All_PCs, method = c("logistic") )
(ctable <- coef(summary(TimeStepPC_OLR)))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
(ctable <- cbind(ctable, "p value" = p))
(ci <- confint(TimeStepPC_OLR))

```

Perfom a logistic regression: PCs ~ sp

```{r}
SP_PC_LogReg <- glm(factor(sp) ~ PC1, data = All_PCs, family = "binomial")

```

plots
```{r}

library("ggplot2")
pdf("PC3_time.pdf")
ggplot(All_PCs, aes(x = time, y = PC3, fill=time)) + 
geom_boxplot() + geom_jitter()+ scale_fill_manual(values=c('#f7fcb9','#41ab5d','#005a32'))+
theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank()) 
dev.off()

pdf("PC3_timeRank.pdf")
ggplot(All_PCs, aes(x = timeRank, y = PC3, color=sp))+
geom_text(aes(label=timeRank),size=10) + scale_color_manual(values=c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854'))+ 
   geom_label()+
theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank()) 
dev.off()

pdf("PC1_PC2.pdf")
ggplot(All_PCs, aes(x = PC1, y = PC2, color=sp)) + 
geom_text(aes(label=timeRank),size=10) + scale_color_manual(values=c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854'))+ 
theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank()) 
dev.off()

pdf("PC3_PC4.pdf")
ggplot(All_PCs, aes(x = PC3, y = PC4, color=sp)) + 
geom_text(aes(label=timeRank), size=10) + 
scale_color_manual(values=c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854'))+
theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank()) 
dev.off()

pdf("PC2_PC4.pdf")
ggplot(All_PCs, aes(x = PC2, y = PC4, color=sp)) + 
geom_text(aes(label=timeRank), size=10) + scale_color_manual(values=c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854'))+
theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank()) 
dev.off()

pdf("PC1_PC4.pdf")
ggplot(All_PCs, aes(x = PC1, y = PC4, color=sp)) + geom_text(aes(label=timeRank), size=10)+
scale_color_manual(values=c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854'))+
theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank()) 
dev.off()

pdf("PC2_PC3.pdf")
ggplot(All_PCs, aes(x = PC2, y = PC3, color=sp)) + 
geom_text(aes(label=timeRank), size=10) + scale_color_manual(values=c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854')) +
theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank()) 
dev.off()

pdf("PC1_PC3.pdf")
ggplot(All_PCs, aes(x = PC1, y = PC3, color=sp)) + 
geom_text(aes(label=timeRank),size=10) + scale_color_manual(values=c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854')) +
theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank()) 
dev.off()

```

Select the 5% highest and 5% lowest loading OGGs for PC3 -- I just selected X from the top and X from the bottom. Then get expression data for those genes. 
```{r}
All_PCloadings<-data.frame(All_PCloadings)
PC3_mostDiff<-All_PCloadings[order(All_PCloadings[,3]),]
PC3_mostDiff<-PC3_mostDiff[c(1:50, 2479:2529),]
PC3_mostDiff_OGGs<-row.names(PC3_mostDiff)


Dan_PC3_mostDiff_exp<-Dan.shared.OGG.exp[,colnames(Dan.shared.OGG.exp)%in%PC3_mostDiff_OGGs] 
Gal_PC3_mostDiff_exp<-Gal.shared.OGG.exp[,colnames(Gal.shared.OGG.exp)%in%PC3_mostDiff_OGGs]
Mus_PC3_mostDiff_exp<-Mus.shared.OGG.exp[,colnames(Mus.shared.OGG.exp)%in%PC3_mostDiff_OGGs]
Xlaev_PC3_mostDiff_exp<-Xlaev.shared.OGG.exp[,colnames(Xlaev.shared.OGG.exp)%in%PC3_mostDiff_OGGs]
Xtrop_PC3_mostDiff_exp<-Xtrop.shared.OGG.exp[,colnames(Xtrop.shared.OGG.exp)%in%PC3_mostDiff_OGGs]
```
Apply the pairwise cor, time steps, and IK time steps and Anova  functions from AllPWcor.Rmd 
```{r}
Dan_Gal_PC3.cor<-PWstageCor(Dan_PC3_mostDiff_exp, Gal_PC3_mostDiff_exp)
Dan_Mus_PC3.cor<-PWstageCor(Dan_PC3_mostDiff_exp, Mus_PC3_mostDiff_exp)
Dan_X.laev_PC3.cor<-PWstageCor(Dan_PC3_mostDiff_exp, Xlaev_PC3_mostDiff_exp)
Dan_X.trop_PC3.cor<-PWstageCor(Dan_PC3_mostDiff_exp, Xtrop_PC3_mostDiff_exp)

Gal_Mus_PC3.cor<-PWstageCor(Gal_PC3_mostDiff_exp, Mus_PC3_mostDiff_exp)
Gal_X.laev_PC3.cor<-PWstageCor(Gal_PC3_mostDiff_exp, Xlaev_PC3_mostDiff_exp)
Gal_X.trop_PC3.cor<-PWstageCor(Gal_PC3_mostDiff_exp, Xtrop_PC3_mostDiff_exp)

X.laev_Mus_PC3.cor<-PWstageCor(Xlaev_PC3_mostDiff_exp,Mus_PC3_mostDiff_exp)
X.trop_Mus_PC3.cor<-PWstageCor(Xtrop_PC3_mostDiff_exp,Mus_PC3_mostDiff_exp)

X.laev_trop_PC3.cor<-PWstageCor(Xlaev_PC3_mostDiff_exp,Xtrop_PC3_mostDiff_exp)

###
Dan_Gal_PC3.TimeCor<-TimeStep15_PWcorMatix(Dan_Gal_PC3.cor,6,5)
Dan_Mus_PC3.TimeCor<-TimeStep19_PWcorMatix(Dan_Mus_PC3.cor,6,4)
Dan_Xlaev_PC3.TimeCor<-TimeStep15_PWcorMatix(Dan_X.laev_PC3.cor,6,4)
Dan_Xtrop_PC3.TimeCor<-TimeStep15_PWcorMatix(Dan_X.trop_PC3.cor,6,4)

Gal_Mus_PC3.TimeCor<-TimeStep19_PWcorMatix(Gal_Mus.cor,5,4)
Gal_Xlaev_PC3.TimeCor<-TimeStep15_PWcorMatix(Gal_X.laev_PC3.cor,5,4)
Gal_Xtrop_PC3.TimeCor<-TimeStep15_PWcorMatix(Gal_X.trop_PC3.cor,5,4)

Xlaev_Mus_PC3.TimeCor<-TimeStep19_PWcorMatix(X.laev_Mus_PC3.cor,4,4)
Xtrop_Mus_PC3.TimeCor<-TimeStep19_PWcorMatix(X.trop_Mus_PC3.cor,4,4)

Xlaev_Xtrop_PC3.TimeCor<-TimeStep15_PWcorMatix(X.laev_trop_PC3.cor,4,4)

All.TimeCor_PC3_Xtrop<-rbind(Dan_Gal_PC3.TimeCor, Dan_Mus_PC3.TimeCor,Dan_Xlaev_PC3.TimeCor, Dan_Xtrop_PC3.TimeCor,Gal_Mus_PC3.TimeCor,Gal_Xlaev_PC3.TimeCor,Gal_Xtrop_PC3.TimeCor,Xlaev_Mus_PC3.TimeCor,Xtrop_Mus_PC3.TimeCor, Xlaev_Xtrop_PC3.TimeCor)

##
library("plyr")
Dan_Gal_PC3.TimeCor_means<-ddply(Dan_Gal_PC3.TimeCor,~time,summarise,cor=mean(cor))
Dan_Mus_PC3.TimeCor_means<-ddply(Dan_Mus_PC3.TimeCor,~time,summarise,cor=mean(cor))
Dan_Xlaev_PC3.TimeCor_means<-ddply(Dan_Xlaev_PC3.TimeCor,~time,summarise,cor=mean(cor))
Dan_Xtrop_PC3.TimeCor_means<-ddply(Dan_Xtrop_PC3.TimeCor,~time,summarise,cor=mean(cor))

Gal_Mus_PC3.TimeCor_means<-ddply(Gal_Mus_PC3.TimeCor,~time,summarise,cor=mean(cor))
Gal_Xlaev_PC3.TimeCor_means<-ddply(Gal_Xlaev_PC3.TimeCor,~time,summarise,cor=mean(cor))
Gal_Xtrop_PC3.TimeCor_means<-ddply(Gal_Xtrop_PC3.TimeCor,~time,summarise,cor=mean(cor))

Xlaev_Mus_PC3.TimeCor_means<-ddply(Xlaev_Mus_PC3.TimeCor,~time,summarise,cor=mean(cor))
Xtrop_Mus_PC3.TimeCor_means<-ddply(Xtrop_Mus_PC3.TimeCor,~time,summarise,cor=mean(cor))

Xlaev_Xtrop_PC3.TimeCor_means<-ddply(Xlaev_Xtrop_PC3.TimeCor,~time,summarise,cor=mean(cor))

All.TimeCor_PC3_means<-rbind(Dan_Gal_PC3.TimeCor_means, Dan_Mus_PC3.TimeCor_means,Dan_Xlaev_PC3.TimeCor_means, Dan_Xtrop_PC3.TimeCor_means,Gal_Mus_PC3.TimeCor_means,Gal_Xlaev_PC3.TimeCor_means,Gal_Xtrop_PC3.TimeCor_means,Xlaev_Mus_PC3.TimeCor_means,Xtrop_Mus_PC3.TimeCor_means, Xlaev_Xtrop_PC3.TimeCor_means)

All.TimeCor_PC3_AOV<-aov(cor~time, data=All.TimeCor_PC3_Xtrop)
summary(All.TimeCor_PC3_AOV)
TukeyHSD(All.TimeCor_PC3_AOV)

#plot
pdf("PC3OGGs_timeCor.pdf")
ggplot(All.TimeCor_PC3_Xtrop, aes(x = time, y = cor, fill=time)) + 
geom_boxplot() + scale_fill_manual(values=c('#f7fcb9','#41ab5d','#005a32'))+ geom_jitter()+
theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank()) 
dev.off()

```
Recreate Irie and Kuratani with PC3 data
```{r}
cor<-c((Dan_Gal_PC3.cor[12,15]), (Dan_Mus_PC3.cor[12,15]), (Dan_X.laev_PC3.cor[12,15]), (Dan_X.trop_PC3.cor[12,15]), (Gal_Mus_PC3.cor[15,19]), (Gal_X.laev_PC3.cor[15,15]), (Gal_X.trop_PC3.cor[15,15]), (X.laev_Mus_PC3.cor[15,19]), (X.laev_trop_PC3.cor[15,15]), (X.trop_Mus_PC3.cor[15,19]))
time<-rep(c('latest'), c(length(cor)))
 
latest_PC3<-data.frame(time,cor)

cor<-c((Dan_Gal_PC3.cor[8,8]), (Dan_Mus_PC3.cor[8,7]),  (Dan_X.laev_PC3.cor[8,10]), (Dan_X.trop_PC3.cor[8,10]), (Gal_Mus_PC3.cor[8,7]), (Gal_X.laev_PC3.cor[8,10]), (Gal_X.trop_PC3.cor[8,10]), (X.laev_Mus_PC3.cor[10,7]), (X.laev_trop_PC3.cor[10,10]), (X.trop_Mus_PC3.cor[10,7]))
time<-rep(c('pharyngula'), c(length(cor)))
 
pharyngula_PC3<-data.frame(time,cor)
 
cor<-c((Dan_Gal_PC3.cor[2,1]), (Dan_Mus_PC3.cor[2,4]),  (Dan_X.laev_PC3.cor[2,3]), (Dan_X.trop_PC3.cor[2,3]), (Gal_Mus_PC3.cor[1,4]), (Gal_X.laev_PC3.cor[1,3]), (Gal_X.trop_PC3.cor[1,3]), (X.laev_Mus_PC3.cor[3,4]), (X.laev_trop_PC3.cor[3,3]), (X.trop_Mus_PC3.cor[3,4]))
time<-rep(c('blastula_shield'), c(length(cor)))
 
blastula_shield_PC3<-data.frame(time,cor)
 
cor<-c((Dan_Mus_PC3.cor[1,2]), (Dan_X.laev_PC3.cor[1,1]), (Dan_X.trop_PC3.cor[1,1]), (X.laev_Mus_PC3.cor[1,2]), (X.laev_trop_PC3.cor[1,1]), (X.trop_Mus_PC3.cor[1,2]))
time<-rep(c('cleavage'), c(length(cor)))
 
cleavage_PC3<-data.frame(time,cor)

IK_timesteps_PC3<-rbind(latest_PC3, pharyngula_PC3, blastula_shield_PC3, cleavage_PC3)
IK_timesteps_PC3_AOV<-aov(cor~time, data=IK_timesteps)
summary(IK_timesteps_PC3_AOV)
TukeyHSD(IK_timesteps_PC3_AOV)

#plot
ggplot(IK_timesteps_PC3, aes(x = time, y = cor, fill=time)) + 
geom_boxplot() + geom_jitter()+ scale_fill_manual(values=c('#f7fcb9','#addd8e','#41ab5d','#005a32'))+ 
  theme(axis.line = element_line(colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank()) 
```
Do PCA for each species independently. Function x = matrix of OGGs by stages, y = total number of stages for ranking.

```{r}
All.shared.OGG.exp<-do.call("rbind", list(Dan.shared.OGG.exp, Gal.shared.OGG.exp, Mus.shared.OGG.exp, Xlaev.shared.OGG.exp, Xtrop.shared.OGG.exp))
  
PCA_timeRanks<-function(x,y){
    x_PCs<-x$x
  t<-as.data.frame(c(1:y))
  colnames(t)<-"timeRank"
  timeRank_PCs<-x_PCs<-cbind(t, x_PCs)
   return(timeRank_PCs)
    }

Dan_PCA<-prcomp(Dan.shared.OGG.exp)
summary(Dan_PCA) #percent variance
Dan_PCs<-PCA_timeRanks(Dan_PCA,15) #timeStep
summary(Dan_PCs)
Dan_PCloadings<-Dan_PCA$rotation





