---
title: "PWcor_of_subset"
author: "Becca"
date: "Friday, September 23, 2016"
output: html_document
---
Extracting OGGs that load the most strongly on "time PCs" across different PCA analyses including: all species, then with each species removed independently. Total of 6 PCA analyses. Top 10% of genes loading on "time PCs" were selected and compared (called "time_TopOGG"). Select those OGGs that are highlighted in at least 4/6 or the analyses.  
```{r}
OGGselect<-function(x,y) {
  #x is a table that has Var1=OGGs that are top 10% of time PCs in at least one PCA
  #y is gene expression values OGG by stage
  x<-as.data.frame(x)
  x<-x[x$Freq %in% c("6"), ] #selects OGGs that are in at least 6/6 
  x<-as.vector(x$Var1)
  z<-y[ , x, drop = FALSE]
  return(z)
  }

```

Apply to all species

```{r, echo=FALSE}
Dan_timeTopOGG<-OGGselect(top.OGGs.freq.table, Dan.shared.OGG.exp)
Gal_timeTopOGG<-OGGselect(top.OGGs.freq.table, Gal.shared.OGG.exp)
Mus_timeTopOGG<-OGGselect(top.OGGs.freq.table, Mus.shared.OGG.exp)
Xlaev_timeTopOGG<-OGGselect(top.OGGs.freq.table, Xlaev.shared.OGG.exp)
Xtrop_timeTopOGG<-OGGselect(top.OGGs.freq.table, Xtrop.shared.OGG.exp)
```

compute all pairwise correlaton (this is from -- AllPWcor.Rmd)
```{r}
PWstageCor<-function(x,y) {
  x<-t(x)
  y<-t(y)
  z<-cor(x,y,use="pairwise.complete.obs", method="spearman")
  return(z)
  }
```


impliment comparaison within lineage to identify time blocks.
```{r}
Gal_Gal_timeTop.cor<-PWstageCor(Gal_timeTopOGG, Gal_timeTopOGG)
Gal_Gal.cor<-PWstageCor(Gal.shared.OGG.exp, Gal.shared.OGG.exp)

Mus_Mus_timeTop.cor<-PWstageCor(Mus_timeTopOGG, Mus_timeTopOGG)
Mus_Mus.cor<-PWstageCor(Mus.shared.OGG.exp, Mus.shared.OGG.exp)

Dan_Dan_timeTop.cor<-PWstageCor(Dan_timeTopOGG, Dan_timeTopOGG)
Dan_Dan.cor<-PWstageCor(Dan.shared.OGG.exp, Dan.shared.OGG.exp)

Xlaev_Xlaev_timeTop.cor<-PWstageCor(Xlaev_timeTopOGG, Xlaev_timeTopOGG)
Xlaev_Xlaev.cor<-PWstageCor(Xlaev.shared.OGG.exp, Xlaev.shared.OGG.exp)

Xtrop_Xtrop_timeTop.cor<-PWstageCor(Xtrop_timeTopOGG, Xtrop_timeTopOGG)
Xtrop_Xtrop.cor<-PWstageCor(Xtrop.shared.OGG.exp, Xtrop.shared.OGG.exp)
```


impliment for all comparisons
```{r}
Dan_Gal_timeTop.cor<-PWstageCor(Dan_timeTopOGG, Gal_timeTopOGG)
Dan_Mus_timeTop.cor<-PWstageCor(Dan_timeTopOGG, Mus_timeTopOGG)
Dan_X.laev_timeTop.cor<-PWstageCor(Dan_timeTopOGG, Xlaev_timeTopOGG)
Dan_X.trop_timeTop.cor<-PWstageCor(Dan_timeTopOGG, Xtrop_timeTopOGG)

Gal_Mus_timeTop.cor<-PWstageCor(Gal_timeTopOGG, Mus_timeTopOGG)
Gal_X.laev_timeTop.cor<-PWstageCor(Gal_timeTopOGG, Xlaev_timeTopOGG)
Gal_X.trop_timeTop.cor<-PWstageCor(Gal_timeTopOGG, Xtrop_timeTopOGG)

X.laev_Mus_timeTop.cor<-PWstageCor(Xlaev_timeTopOGG,Mus_timeTopOGG)
X.trop_Mus_timeTop.cor<-PWstageCor(Xtrop_timeTopOGG,Mus_timeTopOGG)

X.laev_trop_timeTop.cor<-PWstageCor(Xlaev_timeTopOGG,Xtrop_timeTopOGG)


```

Generate a basic heat map for all PW above
```{r} 
#library("RColorBrewer")
library("pheatmap")

#create the breaks
bk2 = unique(c(seq(0, 0.25, length=9), 
               seq(0.251, 0.5, length=9), 
               seq(0.51, 0.75, length=9),
               seq(0.751, 1, length=9)))

#set different color vectors for each interval
col1 = colorRampPalette(c("white", "white"))(9) #set the order 
col2 = colorRampPalette(c("white", 'mistyrose'))(9)
col3 = colorRampPalette(c('mistyrose', 'pink'))(9)
col4 = colorRampPalette(c("pink", "orangered3"))(9)
colors2 <- c(col1, col2, col3, col4)

pdf("AutoCor_AllvTopTime.pdf")
pheatmap(Gal_Gal_timeTop.cor, 
         cluster_rows = FALSE, 
         cluster_cols = FALSE, 
         color = colors2,
         breaks = bk2, 
         main = "Gallus Top Time")
pheatmap(Gal_Gal.cor, 
         cluster_rows = FALSE, 
         cluster_cols = FALSE, 
         color = colors2,
         breaks = bk2, 
         main = "Gallus All")

pheatmap(Mus_Mus_timeTop.cor, 
         cluster_rows = FALSE, 
         cluster_cols = FALSE, 
         color = colors2,
         breaks = bk2, 
         main = "Mus Top Time")
pheatmap(Mus_Mus.cor, 
         cluster_rows = FALSE, 
         cluster_cols = FALSE, 
         color = colors2,
         breaks = bk2, 
         main = "Mus All")

pheatmap(Dan_Dan_timeTop.cor, 
         cluster_rows = FALSE, 
         cluster_cols = FALSE, 
         color = colors2,
         breaks = bk2, 
         main = "Danio Top Time")
pheatmap(Dan_Dan.cor, 
         cluster_rows = FALSE, 
         cluster_cols = FALSE, 
         color = colors2,
         breaks = bk2, 
         main = "Danio All")

pheatmap(Xlaev_Xlaev_timeTop.cor, 
         cluster_rows = FALSE, 
         cluster_cols = FALSE, 
         color = colors2,
         breaks = bk2, 
         main = "Xlaev Top Time")
pheatmap(Xlaev_Xlaev.cor, 
         cluster_rows = FALSE, 
         cluster_cols = FALSE, 
         color = colors2,
         breaks = bk2, 
         main = "Xlaev All")

pheatmap(Xtrop_Xtrop_timeTop.cor, 
         cluster_rows = FALSE, 
         cluster_cols = FALSE, 
         color = colors2,
         breaks = bk2, 
         main = "Xtrop Top Time")
pheatmap(Xtrop_Xtrop.cor, 
         cluster_rows = FALSE, 
         cluster_cols = FALSE, 
         color = colors2,
         breaks = bk2, 
         main = "Xtrop All")
dev.off()
```

Between Species Comparisons
```{r}
pheatmap(Dan_Gal_timeTop.cor, cluster_rows = FALSE, cluster_cols = FALSE)
pheatmap(Dan_Gal.cor, cluster_rows = FALSE, cluster_cols = FALSE)



pheatmap(Dan_Mus_timeTop.cor, cluster_rows = FALSE, cluster_cols = FALSE)
pheatmap(Dan_Mus.cor, cluster_rows = FALSE, cluster_cols = FALSE)



pheatmap(Dan_X.laev_timeTop.cor, cluster_rows = FALSE, cluster_cols = FALSE)
pheatmap(Dan_X.laev.cor, cluster_rows = FALSE, cluster_cols = FALSE)



pheatmap(Dan_X.trop_timeTop.cor, cluster_rows = FALSE, cluster_cols = FALSE)
pheatmap(Dan_X.trop.cor, cluster_rows = FALSE, cluster_cols = FALSE)
dev.off()


pheatmap(Gal_Mus_timeTop.cor, cluster_rows = FALSE, cluster_cols = FALSE)
pheatmap(Gal_Mus.cor, cluster_rows = FALSE, cluster_cols = FALSE)



pheatmap(Gal_X.laev_timeTop.cor, cluster_rows = FALSE, cluster_cols = FALSE)
pheatmap(Gal_X.laev.cor, cluster_rows = FALSE, cluster_cols = FALSE)



pheatmap(Gal_X.trop_timeTop.cor, cluster_rows = FALSE, cluster_cols = FALSE)
pheatmap(Gal_X.trop.cor, cluster_rows = FALSE, cluster_cols = FALSE)



pheatmap(X.laev_Mus_timeTop.cor, cluster_rows = FALSE, cluster_cols = FALSE)
pheatmap(X.laev_Mus.cor, cluster_rows = FALSE, cluster_cols = FALSE)



pheatmap(X.trop_Mus_timeTop.cor, cluster_rows = FALSE, cluster_cols = FALSE)
pheatmap(X.trop_Mus.cor, cluster_rows = FALSE, cluster_cols = FALSE)



pheatmap(X.laev_trop_timeTop.cor, cluster_rows = FALSE, cluster_cols = FALSE)
pheatmap(X.laev_trop.cor, cluster_rows = FALSE, cluster_cols = FALSE)


